### 2015-03-26 draft.tex
Initial draft.

%===============================================================================
% $Id: ifacconf.tex 19 2011-10-27 09:32:13Z jpuente $  
% Template for IFAC meeting papers
% Copyright (c) 2007-2008 International Federation of Automatic Control
%===============================================================================
\documentclass{ifacconf}

\usepackage{graphicx}      % include this line if your document contains figures
\usepackage{natbib}        % required for bibliography
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathrsfs}

\usepackage{todonotes}
\newcommand{\NOTE}[1]{\todo[inline]{#1}}

\newcommand*{\Resize}[1]{\resizebox{\columnwidth}{!}{$#1$}}

\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}

\providecommand{\norm}[1]{\left\|#1\right\|}
\providecommand{\abs}[1]{\left|#1\right|}
\providecommand{\conv}{\text{conv}}

\usepackage{xcolor}
\def\edit{\textcolor{blue}}
\allowdisplaybreaks[4]

%===============================================================================
\begin{document}
\begin{frontmatter}

% predefined environments
%\begin{thm} ... \end{thm}		% Theorem
%\begin{lem} ... \end{lem}		% Lemma
%\begin{claim} ... \end{claim}	% Claim
%\begin{conj} ... \end{conj}	% Conjecture
%\begin{cor} ... \end{cor}		% Corollary
%\begin{fact} ... \end{fact}	% Fact
%\begin{hypo} ... \end{hypo}	% Hypothesis
%\begin{prop} ... \end{prop}	% Proposition
%\begin{crit} ... \end{crit}	% Criterion
%\begin{rem} ... \end{rem}    % Remark
%\begin{pf} ... \end{pf}      % Proof
%\begin{ack} ... end{ack}     % Acknowledgement

\title{Robust receding horizon control for linear systems with state dependent disturbance}

\thanks[footnoteinfo]{Supported by the Martin Senior Scholarship of Worcester College, Oxford.}

\author[Oxford]{Rainer M. Schaich\thanksref{footnoteinfo}} 
\author[Oxford]{Mark Cannon}

\address[Oxford]{Department of Engineering Science, University of Oxford, OX1 3PJ, UK. (e-mail: 
rainer.schaich@eng.ox.ac.uk, mark.cannon@eng.ox.ac.uk).}

\begin{abstract}                % Abstract of not more than 250 words.

\end{abstract}

\begin{keyword}
-
\end{keyword}

\end{frontmatter}
%===============================================================================

\section{Introduction}\label{sec:intro}
Robust model predictive control (RMPC) algorithms compute a control law optimising a performance
criterion subject to state and control constraints for a perturbed system, for all possible realisations of the
perturbation. \cite{Witsenhausen:1968} proposes to formulate the RMPC problem as a game in which the adversary 
tries to maximise the effect of the uncertainty on the cost and the controller chooses its strategy to minimise 
the cost for the worst case system, this formulation is widely accepted, see e.g.~\cite{Bemporad:1999,Bemporad:2003,Lee:1997}.
The worst case system can either be considered to be open-loop, i.e. the controller chooses its strategy for the 
whole horizon before the adversary decides its strategy, or closed-loop, i.e. at each stage along the horizon 
the controller and the adversary play the game for only that stage given the outcome of the previous stage.
Theoretical properties of these controllers are well understood, see e.g.~\cite{Mayne:2000}. However, the
numerical computation of robust model predictive controllers still poses a challenge and only few tractable 
solutions have been proposed.

Numerous strategies have been proposed to solve RMPC problems for linear systems subject to linear state and
input constraints and linearly constrained additive uncertainty.
\NOTE{Do we need to constrain ourselves to additive here? In the literature there are algorithms that cope with
multiplicative just as well..?!}
\cite{Scokaert:1998} propose a scenario-based approach to solve the sequence of min-max problems, however the
complexity grows exponentially with the length of the horizon. A parametrised algorithm was proposed by~\cite{Rakovic:2012}
which can be used to reduce the RMPC problem to a single linear program that can be solved online, bit this 
parametrisation is in general suboptimal. Explicit RMPC algorithms solve the min-max problems offline and exploit 
the structure of the solution using results from multi-parametric programming to parametrise the optimal feedback as 
piecewise affine functions of the state, see e.g.~\cite{Bemporad:2003,Diehl:2004}. However, this requires extensive offline
computation and becomes inefficient for a high dimensional state space. Another approach exploiting the structure
of the solution in the same way but with less redundancy was proposed by~\cite{Buerger:2011} and extended in~\cite{Buerger:ACC},
where an active set solver is designed to solve the sequence of min-max problems explicitly online. In all 
aforementioned papers and, to the authors' best knowledge, in published literature on algorithmic solutions to the RMPC 
problem, the disturbance sets are assumed to be constant, i.e. independent of the system state and control inputs.
Recent algorithmic advances allow us to treat polytopic disturbance sets which depend in an affine way on the system state
and the control input. \cite{Schaich:2015} provide an algorithmic and analytical framework to
embed affine state and input dependent disturbance constraints into the framework of the active set RMPC solver
framework as proposed by~\cite{Buerger:2011}. Disturbance constraints varying with the state and input can be used
to model multiplicative uncertainty as well as linearisation errors which will be shown in an example.

After describing the considered control problem in section~\ref{sec:problem:statement} we summarise preliminary 
results which are necessary to formulate the considered problem explicitly (section~\ref{sec:preliminaries}).
Section~\ref{sec:gen:mpQP} discusses the recursive solution for equality constrained min-max recursions, one of 
the essential parts of the active set solver, it is applied to the considered min-max problem in section~\ref{sec:applied:mpQP}
assuming the active set of constraints is known. A line search to determine the active set of constraints is presented
in section~\ref{sec:line:search}, the application of the proposed algorithm to an example system is presented in 
section~\ref{sec:example}. Conclusions are given in section~\ref{sec:conclusion}.

\section{Problem Statement}\label{sec:problem:statement}
The set of systems to which a min-max robust receding horizon control scheme can be applied online 
without approximating the solution is bounded by the system complexity. The way to solve min-max problems we 
adopt here, is to use the structure of the solution and derive multi-parametric programs that can be solved 
efficiently. In order to be able to obtain a closed form solution of the min-max program simple optimisation 
formulations have to be available, in particular we consider linear constraints. In presence of state constraints 
the algorithmic treatment of state constraints in min-max problems stagnated after it was introduced for fixed 
polytopic disturbance sets by~\cite{Bertsekas:1971}. Recently~\cite{Schaich:2015} proposed an algorithm to compute the
so called maximal robust positive invariant (MRPI) sets (see~\cite{blanchini:2007}) for linear systems subject to state 
and input dependent disturbance constraints is presented. In this paper we develop the algorithm even further allowing 
us to compute polytopic constraints necessary to satisfy state constraints robustly in this setup. We present a 
robust receding horizon control scheme for
%
\begin{equation}\label{eq:system:equation}
	x^+ = A x + B u + D w,
\end{equation}
%
where $A,B,D$ are real matrices of appropriate dimension, $x, x^+\in\mathcal X\subseteq\mathbb R^n$ denote the state 
and successor state respectively, $u\in\mathcal U=\{u:Fu\leq{\bf{1}}\}\subset\mathbb R^p$ the input and $w\in\mathcal W(x,u)
\subset\mathbb R^q$ the disturbance with the state and input dependent disturbance set $\mathcal W(x,u)$. The disturbance 
set $\mathcal W(x,u)$ is defined by
%
\begin{equation}\label{eq:PWA:def:disturbance}
	\mathcal W(x,u) = \{w: Gw \leq H(x,u)\},
\end{equation}
%
where $H(x,u)$ is an element-wise convex piecewise affine function. The min-max optimal control problem
we will optimise is given by the $N$-stage min-max program
%
\begin{subequations}\label{eq:the:problem}%
\begin{equation}
	J_{m}^\ast(x) = \min_u \max_{w,x^+} \tfrac{1}{2}\bigl(\norm{x}_Q^2+\norm{u}_R^2-\gamma^2
    \norm{w}^2\bigr) + J_{m-1}^\ast(x^+)
\end{equation}
subject to
\begin{gather}
	x^+ = A x + B u + D w\\
	u\in\mathcal U \\
	w\in\mathcal W(x,u) \\
	(x,u)\in\mathcal Z_m
\end{gather}
\end{subequations}
%
where we enforce the stage wise state and input constraints $\mathcal Z_m$ in such a way that the terminal state,
i.e. $x^+$ at $m=1$, is contained in the MRPI set $x^+\in\mathcal X^\infty$ for the closed-loop 
system governed by a fixed state feedback controller $u=Kx$. The MRPI set $\mathcal X^\infty$ for this considered
scenario is therefore given by
%
\begin{equation}\label{eq:definition:MRPI:set}
	\mathcal X^\infty = \{x: (A+BK)x + Dw \in \mathcal X^\infty \forall w\in\mathcal W(x,Kx)\}.
\end{equation}
%
subsequently the stage wise constraints $\mathcal Z_m$ are defined recursively as
%
\begin{subequations}\label{eq:definition:stage:constraints}
\begin{align}
	\mathcal Z_m &= \{(x,u)\,: u\in\mathcal U \nonumber\\
	&\quad\ \wedge \; A x + Bu + Dw\in\mathcal X_{m-1}\; \forall\, w\in\mathcal W(x,u)\} 
	\label{eq:definition:mixed:stage:constraint}\\
	\mathcal X_m &= \{x : \exists\, u\in\mathcal U, (x,u)\in\mathcal Z_m\}
	\label{eq:definition:state:stage:constraint}\\
	\mathcal X_0 &= \mathcal X^\infty
\end{align}
\end{subequations}

\section{Preliminaries}\label{sec:preliminaries}
In this section we summarise preliminaries necessary to formulate the considered problem~\eqref{eq:the:problem}
in a convenient way. The point-wise polytopic set defined by~\eqref{eq:PWA:def:disturbance} with a elementwise convex 
piece-wise affine right-hand-side $H$ can be shown to lead to a polytopic MRPI set, see~\cite{Schaich:2015} for an 
elaborate discussion. We summarise the result as we require it in
%
\begin{lem}\label{thm:MRPI:set:is:polytopic}
Let $\mathcal X \subseteq \{x:\Gamma x\leq{\bf{1}}\wedge-\Gamma x\leq{\bf{1}}\}$ polyhedral, and the pair $(A+BK,\Gamma)$ be
observable, furthermore let $\mathcal W(x,Kx)$ be defined as in~\eqref{eq:PWA:def:disturbance} with a elementwise convex piecewise
affine function $H(x,Kx)$ which is bounded for all finite $x$. Then the MRPI set $\mathcal X^\infty$ is a polytope, i.e.
it has the representation 
\begin{equation}\label{eq:halfspace:representation:MRPI}
	\mathcal X^\infty=\{x:\Lambda_i x\leq \lambda_i, \forall\, i\in\mathcal I^\infty\}.
\end{equation}
\end{lem}
%
We need to emphasise the following 
\begin{rem}\label{rem:vertex:representation}
Notice that one essential assumption in Lemma~\ref{thm:MRPI:set:is:polytopic} is that $\mathcal W(x,u)$ is a polytope
for all finite $(x,u)$, i.e. it has a convex hull representation $\mathcal W(x,u) = \conv_k\{w_k(x,u)\}, k\in\{1,\dots,r\}$ where each 
vertex~$w_k(x,u)$ is a piecewise affine function in $(x,u)$,i.e.
\begin{equation}
\Resize{
	w_k(x,u) = \max\{W_{k,1}^x x + W_{k,1}^u u + w_{k,1},W_{k,2}^x x + W_{k,2}^u u + w_{k,2},\dots\}
}
\end{equation}
where the maximisation is done elementwise.
\end{rem}
%
We now derive the representation of $\mathcal Z_m$ and $\mathcal X_m$ as defined in~\eqref{eq:definition:stage:constraints}.
According to Lemma~\ref{thm:MRPI:set:is:polytopic} the MRPI set $\mathcal X^\infty$ is polytopic and has the 
representation~\eqref{eq:halfspace:representation:MRPI}, the recursion~\eqref{eq:definition:mixed:stage:constraint}
therefore defines $\mathcal Z_1$ as
\begin{equation}\label{eq:derivation:of:mpLP:stage:constraints}
\Resize{
\begin{aligned}
	\mathcal Z_1 =& (\mathbb R^n\times\mathcal U)\cap\\
	&\{(x,u):\Lambda_{0,i}(Ax+Bu+Dw)\leq\lambda_{0,i} \forall w\in\mathcal W(x,u),i\in\mathcal I_0\}\\
	=&(\mathbb R^n\times\mathcal U)\cap\\
	&\left\{\vphantom{\max_{w}}\right.
	(x,u):\max_{w\in\mathcal W(x,u)}\Lambda_{0,i}(Ax+Bu+Dw)\leq\lambda_{0,i}\forall i\in\mathcal I_0
	\left.\vphantom{\max_w}\right\}\\
	=&(\mathbb R^n\times\mathcal U)\cap\\
	&\left\{\vphantom{\max_{w}}\right.
	\Lambda_{0,i}(Ax+Bu)+ \underbrace{\max_{j\in\{1,\dots,r\}}\Lambda_{0,i} Dw_j(x,u)}_{(I)}\leq\lambda_i\forall i\in\mathcal I_0
	\left.\vphantom{\max_w}\right\}
\end{aligned}
}
\end{equation}
The maximisation~$(I)$ in~\eqref{eq:derivation:of:mpLP:stage:constraints} is a multi-parametric
linear program, its solution is piecewise affine. Therefore the set $\mathcal Z_1$ has a representation
$\mathcal Z_1=\{(x,u):\Xi^x_{1,i}x+\Xi^u_{1,i}u\leq\xi_{1,i},i\in\mathcal J_1\}$, its projection~$\mathcal X_1$ 
onto~$\mathbb R^n$ is therefore has the representation~$\mathcal X_1 = \{x:\Lambda_{1,i} x\leq\lambda_{1,i},i\in\mathcal I_1\}$.
From here the determination of $\mathcal Z_k$ and $\mathcal X_k$ follows recursively. We are now able to formulate 
all constraints in~\eqref{eq:the:problem} as inequalities. In the next section we discuss a method of solving
min-max programs such as~\eqref{eq:the:problem} efficiently.

\section{Solving equality constrained multi-parametric quadratic programs}\label{sec:gen:mpQP}
In this section we discuss equality constraint multi-parametric quadratic programs (mpQP) 
(see~\cite{bemporad02,Tondel:2003} for an extended discussion), as they are essential in the treatment 
of the considered min-max program using an active set solver. Note that the notation in this section does 
not refer to the notation in the preceding and proceeding sections.

Consider the primal equality-constrained concave mpQP
\begin{equation}\label{mpQP:primal}
	V(\theta) = \left\{\begin{split}
	\max_x & \;\frac{1}{2} x^T W x + c^Tx + d\\
	\text{s.t.} &\; Hx  = f +S\theta
	\end{split}\right.
\end{equation}
for $W\preceq 0.$ The Lagrangian function associated with~\eqref{mpQP:primal} is
\begin{equation}
	L(x,\lambda,\theta)  = \frac{1}{2} x^T W x + c^Tx + d + \lambda^T(Hx - f - S\theta)
\end{equation}
and the dual problem is the unconstrained mpQP
\begin{equation}\label{mpQP:dual}\begin{split}
	\min_\lambda &\; \mathcal D(\lambda,\theta)= \min_\lambda-\frac{1}{2}\lambda^T H W^{-1}H^T \lambda 
	-(HW^{-1}c\\ &+ f + S\theta)^T\lambda
	-\frac{1}{2}c^TW^{-1}c +d
\end{split}\end{equation}
To solve~\eqref{mpQP:primal} we consider the first order optimality conditions, see e.g.~\cite{Fletcher:2000}:
\begin{equation}\label{kkt:conditions}
	\begin{aligned}
        W x + H^T\lambda & = -c \\
        H x &= f + S\theta.
	\end{aligned}
\end{equation}

\begin{thm}\label{thm:mpQP:solution}
The solution of~\eqref{kkt:conditions} has the representation
\begin{equation}\label{mpQP:solution}
	\begin{split}
		x &= M_\theta \theta + m\\
		\lambda &= N_\theta \theta + N_\beta \beta + n
	\end{split}
\end{equation}
where $N_\beta\neq 0$ only if $H$ is rank deficient, in which case the rows
of $N_\beta$ form a basis of the kernel of $H$, i.e. $H^TN_\beta=0$
\end{thm}
%
The matrices~$M_\theta$, $N_\theta$, $N_\beta$ as well as the vectors $m$ and $n$
are constant, the variable $\beta$ is used to parametrise the solution in the null space of~\eqref{kkt:conditions}.
%
\begin{pf}
There are two cases of rank deficient $H$: rank$(H)=n_x<n_\lambda$ and
rank$(H)<\min\{n_x,n_\lambda\}$.
Using the QR-decomposition (see e.g.~\cite{Nocedal:2006}) of $H=(Q_1,Q_2)\cdot(R^T,0)^T$ the solution 
is given by $(m^T,n^T)^T = \Sigma (-c^T,f^T)^T$, $(M_\theta^T,N_\theta^T)^T = 
\Sigma (0,S^T)^T$ and $N_\beta=Q_2$, where 
\begin{equation}
	\Sigma = \left(\begin{array}{cc}
	0 & R^{-1}Q_1^T \\
	Q_1 R^{-T} & -Q_1R^{-T}WR^{-1}Q_1^T
	\end{array}\right)
\end{equation}
in the case where the number of equality constraints is larger than the dimension of
the primal variable, i.e. rank$(H)=n_x$. If rank$(H)<\min\{n_x,n_\lambda\}$, so that $R$ is
not invertible, then
\begin{equation}
	\Sigma = \left(\begin{array}{cc}
	W^{-1}-W^{-1}R^T\Delta RW^{-1} & W^{-1}R^{T}\Delta Q_1^{T}\\
	Q_1\Delta R W^{-1} & -Q_1\Delta Q_1^T
	\end{array}\right)
\end{equation}
with $\Delta = (RW^{-1}R^T)^{-1}$. This concludes the proof.
\end{pf}
%
Since the degeneracy variable $\beta$ does not appear in the
primal optimiser, it does not affect the primal objective value of~\eqref{mpQP:primal}.
However, substituting~\eqref{mpQP:solution} into the dual objective~\eqref{mpQP:dual} yields
\begin{multline}
    \mathcal D(\lambda(\theta,\beta),\theta) =  -\frac{1}{2}(N_\theta \theta + N_\beta \beta + n)^T H W^{-1}H^T 
	(N_\theta \theta\\ + N_\beta \beta + n)
	-(AW^{-1}c + 
	f + S\theta)^T(N_\theta \theta + N_\beta \beta + n)\\ -\frac{1}{2}c^TW^{-1}c,
\end{multline}
which is unbounded if
\begin{equation}
	(f^T+\theta^TS^T)N_\beta \neq 0
\end{equation}
and can be made arbitrarily small by the choice of $\beta$. Therefore we restrict $\theta$ to satisfy 
\begin{equation}\label{mpQP:compatability:assumption}
	N_\beta^Tf = -N_\beta^TS\theta,
\end{equation} 
so that the dual mpQP has a unique solution
and the choice of $\beta$ does not affect either the primal nor the dual cost and can be used for
any purpose. For a general mpQP~\eqref{mpQP:compatability:assumption} is a restriction on the set
of parameters for which~\eqref{mpQP:primal} has a solution of the form~\eqref{mpQP:solution}.
In our multi-stage min-max setup, the parameter is the optimiser of a subsequent optimisation
problem and can be ensured to satisfy~\eqref{mpQP:compatability:assumption} by the so called 
compatibility constraint. The optimal objective of~\eqref{mpQP:primal} is given by
\begin{equation}\label{mpQP:cost:to:go}\begin{split}
	V(\theta) = &\frac{1}{2}\theta^T M_\theta^T W M_\theta \theta + c^TM_\theta \theta
\\&+ m^TWM_\theta+\frac{1}{2}m^T Wm + c^Tm\\
=&\frac{1}{2} \theta^T W_\theta \theta + c^T_\theta \theta + d_\theta.
\end{split}\end{equation}
%
Assume now that we want to solve
\begin{equation}\label{mpQP:second:stage}
	J(\phi) = \left\{\begin{array}{rl}
	\min_\theta & \frac{1}{2}\theta^T\Phi\theta + g^T\theta + f + V(\theta)\\
	\text{s.t.} & C\theta = e+T\phi
	\end{array}\right.
\end{equation}
where the equality constraints include~\eqref{mpQP:compatability:assumption}. Since we know
that the optimal cost-to-go $V(\theta)$ has the structure~\eqref{mpQP:cost:to:go}
the problem~\eqref{mpQP:second:stage} reduces to a problem like~\eqref{mpQP:primal},
which yields a solution like~\eqref{mpQP:solution}, i.e.
\begin{equation}
\begin{split}
	\theta &= K_\phi \phi + k\\
	\eta &= L_\phi \phi + L_{\hat\beta} \hat\beta + l
\end{split}
\end{equation}
with the dual variable~$\eta$, as long as $\Phi+W_\theta\succ 0$. Finally we note 
that~\eqref{mpQP:compatability:assumption} is only nontrivial if~$H$ is rank deficient and only 
introduces as many constraints on~$\theta$ as there are linearly
dependent rows in~$H$.

In the solution of recursive min-max programs such as~\eqref{eq:the:problem} we use the composition of
the stage optimisers, i.e. we use $x(\theta(\phi)) = M_\theta K_\phi \phi + (M_\theta k + m)$.
Notice that this composition of optimisers is again an affine function of the parameter, in particular
we will exploit the fact that changing the parameter along a line will translate to a line in the optimiser
space as long as no activations or deactivations in the constraints occur. We will revisit this fact
when we perform a line search in order to update the active constraints.

\section{Solving min-max quadratic programs as multi-parametric quadratic programs}\label{sec:applied:mpQP}
In this section we apply the results derived in section~\ref{sec:gen:mpQP} to
the considered min-max robust control problem~\eqref{eq:the:problem}. We 
define a recursion and assume the active set is known to obtain a closed solution for~\eqref{eq:the:problem}.
%
To use an active set solver for the problem:
\begin{subequations}\label{eq:the:problem:reformulated}%
\begin{equation}
	J_{m}^\ast(x) = \min_u \max_{w,x^+} \tfrac{1}{2}\bigl(\norm{x}_Q^2+\norm{u}_R^2-\gamma^2
    \norm{w}^2\bigr) + J_{m-1}^\ast(x^+)
\end{equation}
subject to
\begin{gather}
	x^+ = A x + B u + D w
\\
\label{eq:dist:cons}
	G w \leq  H(x,u)
\\
\label{eq:state:constraints}
	\Xi^x_m x + \Xi^u_m u \leq \xi_m
\\
	\hat C_m x^+ = - {\bf{1}}
\\
	C_m^x x + C_m^u u  = {\bf{1}}
\end{gather}
\end{subequations}
with~$J_0^\ast(x^+) = \frac{1}{2}\norm{x^+}_P^2$ and $m=1,\dots,N$. Notice that explicitly using
$u\in\mathcal U$ is no longer necessary as satisfaction of the input constraints is intrinsic
if $(\cdot,u)\in\mathcal Z_m$.
We split the sequence of  min-max problems into a sequence of multi-parametric 
quadratic programs. Starting with the maximisation at stage $m=1$ and using a backward sweep approach (see e.g.~\cite{Bryson:1975}), 
we obtain
\begin{equation}
	\hat J_m^\ast(x,u) = \left\{\begin{split}
    \max_{w,x^+} & -\frac{\gamma^2}{2}\norm{w}^2 + J_{m-1}^\ast(x^+)\\
    \text{s.t.} & \begin{array}{rcl}
    Gw & \leq & H(x,u)\\
    x^+ & = & Ax + Bu + Dw\\
    \hat C_m x^+ &=& -{\bf{1}}
    \end{array}
    \end{split}\right.
\end{equation}
and
\begin{equation}
	J_m^\ast(x) = \left\{\begin{split}
    \min_{u} & \frac{1}{2}\left(\norm{x}^2_Q + \norm{u}_R^2\right) + \hat J_m^\ast(x,u)\\
    \text{s.t.} & \begin{array}{ccccl}
    \Xi^x_m x &+& \Xi^u_m u &\leq &\xi_m\\
    C_m^x x &+ & C^u_m u & = & {\bf{1}}
    \end{array}
    \end{split}
    \right.
\end{equation}
Suppose the active set is given, i.e.~it is known which inequality constraints hold with equality. 
For notational convenience we denote active inequalities with $(\cdot)^\prime$, e.g.  $(\Xi^x_m)^\prime x + (\Xi^u_m)^\prime u = \xi_m^\prime$. 
Since $J^\ast_0(x^+) = \frac{1}{2}\norm{x^+}_{P_0}^2$ is a given function, compatibility constraints are not necessary at 
stage $m=1$ and the maximisation problem is given by:
\begin{equation}
	\hat J_1^\ast(x,u) = \left\{\begin{split}
	\max_{w,x^+} & -\frac{\gamma^2}{2}\norm{w}^2 + J_{0}^\ast(x^+)\\
	\text{s.t.} & 
	\underbrace{\left(\begin{array}{cc}
	G^\prime & 0 \\ -D & I
	\end{array}\right)}_{\bar H}
	\left(\begin{array}{c}w\\ x^+\end{array}\right)
	\\&= \underbrace{\left(\begin{array}{cc}W_x^\prime & W_u^\prime \\ A & B\end{array}\right)}_{
	\bar S
	}
	\left(\begin{array}{c}x \\ u \end{array}\right) + \underbrace{\left(\begin{array}{c}
	w_c^\prime \\ 0\end{array}\right)}_{\bar f}
	\end{split}\right.
\end{equation}
with $W_x^\prime, W_u^\prime$ and $w_c^\prime$ denoting the active rows of the right hand side 
of~\eqref{eq:dist:cons}.
With Lemma~\ref{thm:mpQP:solution} we obtain
\begin{equation}
      \left(\begin{array}{c}
      w^\ast \\
      x^{+,\ast} \\
      \eta^\ast \\
      \lambda^\ast
      \end{array}\right) = \left(\begin{array}{c}M^w_z\\ M^{x^+}_z \\ N^{\eta}_z \\ N^{\lambda}_z
      \end{array}\right)\underbrace{\left(\begin{array}{c}x\\ u\end{array}\right)}_z + 
      \left(\begin{array}{c}0\\ 0 \\ N^{\eta}_{\hat\beta} \\ N^{\lambda}_{\hat\beta}
      \end{array}\right)\hat\beta + \left(\begin{array}{c}m^w\\ m^{x^+} \\ n^{\eta} \\ n^{\lambda}
      \end{array}\right)
\end{equation}
where $\eta^\ast$ denotes the dual variable to the active inequality constraints and hence must
be non-negative, i.e.~$\eta^\ast\geq0$. Notice that we omitted stage indices to avoid overloaded notation.
The cost-to-go for the minimisation problem at stage $m=1$ is
\begin{equation}
	\hat J_1^\ast(z) = \frac{1}{2}z^T
    \hat Q_1 z + c_1 z + d_1
\end{equation}
and the compatibility constraint is given by
\begin{equation}\label{prototype:compatibility:conditions}
	N_{\hat\beta}^T(\bar S z + \bar f) = 0,
\end{equation}
i.e.\ $C_1^x$ and $C_1^u$ are given as a row wise normalised version of~\eqref{prototype:compatibility:conditions}.
Hence the minimisation problem at $m=1$ becomes
\begin{equation}
	J_1^\ast(x) = \left\{\begin{split}
	\min_{u} & \frac{1}{2}\left(\norm{x}^2_Q + \norm{u}_R^2\right) + \hat J_{1}^\ast(x,u)\\
    \text{s.t.} & 
    \underbrace{\left(\begin{array}{c}
    (\Xi_1^u)^\prime \\ C_1^u
    \end{array}\right)}_{\bar C}
    u
    = \underbrace{\left(\begin{array}{c}-(\Xi^x_1)^\prime \\ -C_1^x\end{array}\right)}_{
    \bar T
    }x + 
    \underbrace{\left(\begin{array}{c}\xi_1^\prime\\  {\bf{1}} \end{array}\right)}_{\bar e}
    \end{split}\right.
\end{equation}
and its solution is given by
\begin{equation}
	\left(\begin{array}{c}
	u^\ast \\
	\nu^\ast \\
	\hat\zeta^\ast
	\end{array}\right) = \left(\begin{array}{c}K^u_x\\ O^{\nu}_x \\ O^{\hat\zeta}_x
	\end{array}\right)x + 
	\left(\begin{array}{c}0\\ O^{\nu}_\beta \\ O^{\hat\zeta}_{\beta}
	\end{array}\right)\beta + \left(\begin{array}{c}k^u\\ o^{\nu} \\ o^{\hat\zeta}
	\end{array}\right).
\end{equation}
Here $\hat C_2$ is a normalised version of $O^T_\beta(\bar T x + \bar e) = 0$.
For completeness, the $m=2$ maximisation and its solution are:
\begin{equation}
	\hat J_2^\ast(x,u) = \left\{\begin{split}
	\max_{w,x^+} & -\frac{\gamma^2}{2}\norm{w}^2 + J_{1}^\ast(x^+)\\
	\text{s.t.} & 
	\underbrace{\left(\begin{array}{cc}
	G^\prime & 0 \\ -D & I \\
	0 & \hat C_2
	\end{array}\right)}_{\bar A}
	\left(\begin{array}{c}w\\ x^+\end{array}\right)
	\\&= \underbrace{\left(\begin{array}{cc}W_x^\prime & W_u^\prime \\ A & B \\ 0 & 0\end{array}\right)}_{
	\bar S
	}
	\left(\begin{array}{c}x \\ u \end{array}\right) + \underbrace{\left(\begin{array}{c}
	w_c^\prime \\ 0 \\ {\bf{1}}\end{array}\right)}_{\bar b}
	\end{split}\right.
\end{equation}
\begin{equation}
	\left(\begin{array}{c}
	w^\ast \\
	x^{+,\ast} \\
	\eta^\ast \\
	\lambda^\ast\\
	\zeta^\ast
	\end{array}\right) = \left(\begin{array}{c}M^w_z\\ M^{x^+}_z \\ N^{\eta}_z \\ N^{\lambda}_z \\ N^{\zeta}_z
	\end{array}\right)z + 
	\left(\begin{array}{c}0\\ 0 \\ N^{\eta}_{\hat\beta} \\ N^{\lambda}_{\hat\beta} \\ N^\zeta_{\hat\beta}
	\end{array}\right)\hat\beta + \left(\begin{array}{c}m^w\\ m^{x^+} \\ n^{\eta} \\ n^{\lambda}\\ n^\zeta
	\end{array}\right)
\end{equation}
All subsequent minimisations and maximisations can be solved analogously provided the active set is
known.

\section{Exact solution of min-max program}\label{sec:line:search}
In the previous section we presented a recursive algorithm to solve~\eqref{eq:the:problem}
when all active constraints are known. In this section we present a method to find the active
constraints for a given initial state $\mathpzc x_e$ using a line search starting from a state $\mathpzc x_0$
for which the active constraints are known. In section~\ref{sec:gen:mpQP} and~\ref{sec:applied:mpQP}
we derived an explicit solution for each sub-optimisation program which depended affinely on the
state~$x$ at that stage~$m$ or the state and the input at that stage. Henceforth we denote the stage 
with an index, e.g.~$x_m$ denotes the optimised state in stage $m$, that is $x^{+,\ast}$ at stage $m+1$.
To ensure continuity of the dual variables we choose $\hat\zeta_m = \hat\beta_m$ and $\zeta_m=\beta_{m-1}$.
The affine character of the solution of each sub-problem allows us to parametrise the entire trajectory
with respect to parameters at stage~$m=N$, that is $x_N=\mathpzc x_0$ and $\beta_N$.

We recursively define all primal and dual variables:
\begin{equation}\label{eq:trajectory:affine:representation}
	\begin{split}
		u_N(x_N) =& \underbrace{K_{x,N}^x}_{\Psi_N^u} x_N + \underbrace{k_N^u}_{\psi_N^u}\\
		\nu_N(x_N,\beta_N) &= \underbrace{O_{x,N}^x}_{\Psi_N^\nu} x_N + \underbrace{O_{\beta,N}^\nu}_{\Phi_N^\nu} \beta_N + 
		\underbrace{o_N^\nu}_{\psi_N^u}\\
		&\vdots \\
		x_0(x_N) =& \underbrace{M_{z,1}^{x^+}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right)}_{\Psi_1^x}x_N + 
		M_{z,1}^{x^+}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + m_1^{x^+}\\
		\eta_1(x_N,\beta_N) =& \underbrace{\left(N_{z,1}^{\eta}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right) + 
		N_{\hat\beta,1}^\eta \Psi_1^{\hat\zeta}\right)}_{\Psi_1^\eta}x_N + \underbrace{N_{\hat\beta,1}^\eta \Phi_1^{\hat\zeta}}_{\Phi_1^\eta} \beta_N\\
		&+\underbrace{N_{z,1}^{\eta}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + 
		N_{\hat\beta,1}^\eta \psi_1^{\hat\zeta} + n_1^\eta}_{\psi_1^\eta}\\
		&\vdots
	\end{split}
\end{equation}
Notice that $\Phi^{(\cdot)}_m$ is only non-trivial if the associated sub-problem is degenerate. The 
representation~\eqref{eq:trajectory:affine:representation} is valid as long as the constraint set remains unchanged, 
i.e. the inequalities that hold with equality do not change. Starting from the known set of active constraints at
$\mathpzc x_0$ we perform a line search towards $\mathpzc x_e$, i.e. we vary $x_N(\alpha)=\mathpzc x_0+
\alpha(\mathpzc x_e-x_0)$ for $0\leq\alpha\leq1$. We use~\eqref{eq:trajectory:affine:representation} to
check all inactive constraints with the primal variables $x_m(x_N(\alpha)),\, u_m(x_N(\alpha))$ and~$w_m(x_N(\alpha))$,
and all dual variables corresponding to inequality constraints to check whether constraints need to be deactivated. That is,
we search for the smallest $\alpha$ such that $\Xi_{m,i}^x x_m(x_N(\alpha))+\Xi_{m,i}^u u_m(x_N(\alpha))=\xi_{m,i}$
et cetera for the primal variables and the smallest $\eta_{m,i}(x_N(\alpha),\beta_N)=0$ and update the set of active
constraints accordingly, i.e. if an additional constraint is activated it is introduced to the equality constraint
mpQP recursion and the updated problems are solved again recursively, if a constraint needs to be deactivated
because the smallest $\alpha$ corresponds to the zero-crossing of its dual variable then again the mpQP recursion 
is solved again. The updated active set is the new known active set at $\mathpzc x_0 = x_N(\alpha)$ and the line-search
continues until the state~$\mathpzc x_e$ is in the same active set as $\mathpzc x_N(\alpha)$ where the line-search terminates.
To initialise we start at the origin $\mathpzc x_0=0$, since we know that no constraints are active. Notice that the right hand side 
of~\eqref{eq:dist:cons} is updated the same way, a line-search is used to determine the active affine representation.

If there are compatibility constraints on the initial state, i.e.\ if $\beta_N$ is non-trivial, then $\alpha$ cannot continue 
to  increase since equality constraints on $x_N(\alpha)$ are active, however $\beta_N$ can be used to update the active set. 
As in~\cite{Buerger:ACC} the free degeneracy variable $\beta_N$ is chosen to deactivate an active constraint on $x_N(\alpha)$ 
as long as no inequality constraints would be violated, i.e. as long as no dual variable becomes negative.

\section{Example}\label{sec:example}
This section we present a numerical simulation in which the state-dependent uncertainty enters through an upper bound on the linearisation
error for a nonlinear system. We consider an inverted pendulum described by $ml^2\ddot\varphi = mlg\sin\varphi+M$, where
$m=0.1$\,kg is the mass, $l=0.3$\,m is the length of the pendulum, $g=9.81$\,m\,s$\mbox{}^{-2}$ is the gravitational
constant and $M$ is the direct torque input. Discretisation using Euler backward finite differences 
at $f = 20$\,Hz yields
\begin{equation}
  \begin{split}
    x_1[k+1] &= x_1[k] + \frac{1}{f} x_2[k]\\
    x_2[k+1] &= \frac{g}{fl} \sin(x_1[k]) + x_2[k] + \frac{1}{fml^2}u[k]
  \end{split}
\end{equation}
where $x_1[k] = \varphi(t_0+k/f),x_2[k] = \dot\varphi(t_0+k/f)$ and $u[k] = M(t_0+k/f)$.
The nonlinearity is given by the sine function, and we can explicitly state the 
linearisation error as $e(x_1)=\frac{g}{fl}(\sin x_1 - x_1)$. Since the linearisation
only approximates the nonlinear dynamics around the equilibrium we can choose a closed interval 
$0\in D\subset\mathbb R$ and maximise the upper bound 
\begin{equation}
  \Delta e = \max_{x_1\in D}\abs{\frac{de}{dx_1}} = \frac{g}{fl}\max_{x_1\in D}\abs{\cos x_1-1}.
\end{equation}
This results in the linear system
\begin{equation}
  x^+ = \underbrace{\left(\begin{array}{cc}
  1 & f^{-1}\\ g(fl)^{-1} & 1
  \end{array}\right)}_A x + \underbrace{\left(\begin{array}{c} 0 \\(ml^2f)^{-1} \end{array}\right)}_B u
  +\left(\begin{array}{c}w_1\\ w_2\end{array}\right)
\end{equation}
with $\abs{w_1}\leq w_{1,\max}$ and $\abs{w_2}\leq\max\{w_{2,\max},\Delta e \abs{x_1}\}$.
We also introduce the input constraint $\abs{u}\leq3$\,N\,m and use the interval $D = [-\frac{3\pi}{4},
\frac{3\pi}{4}]$ and a horizon of $N=7$ to obtain the sequence of state constraints $\mathcal X_m$
depicted in Figure~\ref{fig:numerical:example}. The line search starting at the origin and
exploring towards $\mathpzc x_e=(-6,50)$ produces the optimal trajectories at the active-set switches
which are illustrated in blue. In pink a warm-started line search terminates on the boundary of the
feasible set before reaching the (infeasible) state $\mathpzc x_e=(0,30)$.

\begin{figure}
\includegraphics[width=.48\textwidth]{res}
\caption{The light blue sets depict the projected state constraint iterates~$\mathcal X_m$,
    whereas the blue and pink lines are the state trajectories produced along the two line
    searches. The pink line search eventually violates the state constraints and terminates.}
\label{fig:numerical:example}
\end{figure}
\section{Conclusion}\label{sec:conclusion}

\bibliographystyle{ifacconf}        % Include this if you use bibtex 
\bibliography{MyLib}       % and a bib file to produce the 
								                 % bibliography (preferred). The
                                 % correct style is generated by
                                 % Elsevier at the time of printing.

\end{document}

### 2015-04-08 draft.tex
Added note on mpLP for rhs of dist constraint.

@@
 continues until the state~$\mathpzc x_e$ is in the same active set as $\mathpzc x_N(\alpha)$ where the line-search terminates.
-To initialise we start at the origin $\mathpzc x_0=0$, since we know that no constraints are active. Notice that the right hand side 
-of~\eqref{eq:dist:cons} is updated the same way, a line-search is used to determine the active affine representation.
+To initialise we start at the origin $\mathpzc x_0=0$, since we know that no constraints are active.
+
+Notice that in since the right hand side of~\eqref{eq:PWA:def:disturbance} is considered to be piecewise affine, the active 
+affine function needs to be determined in a similar fashion. Elementwise $H(x_k(\alpha),u_k(\alpha))$ reduces to 
+\begin{equation}
+\Resize{
+\begin{split}
+	H_i(x_k(\alpha),u_k(\alpha)) &= \max_j\{\left(H^x_{i,j} \Psi^x_k +H^u_{i,j}\Psi^u_k\right)x_N(\alpha) + 
+	\left(H^x_{i,j} \psi^x_k +H^u_{i,j}\psi^u_k + h_{i,j}\right) \}\\
+	&=\max_j f_j\alpha + g_j
+	\end{split}
+}
+\end{equation}
+which we can rewrite as
+\begin{equation}\label{eq:definition:as:mpLP}
+	H_i(x_k(\alpha),u_k(\alpha)) = \left\{\begin{array}{rcl} \min_{(t,\alpha)}& &t\\
+	\text{s.t.}& &f_j\alpha+g_j \leq t\; \forall j.\\
+	& &0\leq\alpha\leq1
+	\end{array}\right.
+\end{equation}
+So elementwise the determination of the active affine representation is a multi-parametric linear program
+that has to be solved in every active set update. So that $W_x^\prime,\,W_u^\prime$ and $w^\prime_c$ remain the active
+solution. This can be done by computing the vertices of $\mathcal H = \{(t,\alpha):0\leq\alpha\leq1\wedge
+f_j\alpha+g_j\leq t\;\forall j\}$ and ordering the vertices such that $0=\alpha_1\leq\alpha_2\leq\dots$ the solution
+that has to be considered in the line search is given by $\alpha_2$.
 

### 2015-04-08 draft.tex
Added citation.

@@
 \end{equation}
-So elementwise the determination of the active affine representation is a multi-parametric linear program
+So elementwise the determination of the active affine representation is a multi-parametric linear program, see e.g.~\cite{Gal:1995},
 that has to be solved in every active set update. So that $W_x^\prime,\,W_u^\prime$ and $w^\prime_c$ remain the active

### 2015-04-20 draft_v2.tex
edited sections 1-3

--- 2015-04-08 draft.tex
@@
 \section{Introduction}\label{sec:intro}
-Robust model predictive control (RMPC) algorithms compute a control law optimising a performance
-criterion subject to state and control constraints for a perturbed system, for all possible realisations of the
-perturbation. \cite{Witsenhausen:1968} proposes to formulate the RMPC problem as a game in which the adversary 
-tries to maximise the effect of the uncertainty on the cost and the controller chooses its strategy to minimise 
-the cost for the worst case system, this formulation is widely accepted, see e.g.~\cite{Bemporad:1999,Bemporad:2003,Lee:1997}.
-The worst case system can either be considered to be open-loop, i.e. the controller chooses its strategy for the 
-whole horizon before the adversary decides its strategy, or closed-loop, i.e. at each stage along the horizon 
-the controller and the adversary play the game for only that stage given the outcome of the previous stage.
-Theoretical properties of these controllers are well understood, see e.g.~\cite{Mayne:2000}. However, the
-numerical computation of robust model predictive controllers still poses a challenge and only few tractable 
-solutions have been proposed.
+
+Robust model predictive control (RMPC) algorithms compute a control law that optimises a predicted performance
+criterion subject to state and control constraints for all possible realisations of model
+uncertainty. \citet{Witsenhausen:1968} proposes to formulate the RMPC problem as a game in which the adversary
+tries to maximise the effect of model uncertainty on the cost and the controller chooses its strategy to
+minimise the cost for the worst case system parameters and disturbances. This formulation is widely accepted
+in the RMPC literature \citep[e.g.][]{Bemporad:1999,Bemporad:2003,Lee:1997}.
+%see e.g.~\cite{Bemporad:1999,Bemporad:2003,Lee:1997}.  
+The predicted control law may be an open-loop policy, in which case the controller chooses its strategy for
+the whole prediction horizon before the adversary decides its strategy, or a closed-loop policy in which the
+horizon is split into stages and the actions of controller and adversary at each stage depend on the
+outcome of the previous stage).
+Theoretical properties of these controllers are well understood \citep[e.g.][]{Mayne:2000}.
+However, the numerical computation of robust model predictive controllers still poses
+a challenge and only few tractable solutions have been proposed.
 
 Numerous strategies have been proposed to solve RMPC problems for linear systems subject to linear state and
-input constraints and linearly constrained additive uncertainty.
-\NOTE{Do we need to constrain ourselves to additive here? In the literature there are algorithms that cope with
-multiplicative just as well..?!}
-\cite{Scokaert:1998} propose a scenario-based approach to solve the sequence of min-max problems, however the
-complexity grows exponentially with the length of the horizon. A parametrised algorithm was proposed by~\cite{Rakovic:2012}
-which can be used to reduce the RMPC problem to a single linear program that can be solved online, bit this 
-parametrisation is in general suboptimal. Explicit RMPC algorithms solve the min-max problems offline and exploit 
-the structure of the solution using results from multi-parametric programming to parametrise the optimal feedback as 
-piecewise affine functions of the state, see e.g.~\cite{Bemporad:2003,Diehl:2004}. However, this requires extensive offline
-computation and becomes inefficient for a high dimensional state space. Another approach exploiting the structure
-of the solution in the same way but with less redundancy was proposed by~\cite{Buerger:2011} and extended in~\cite{Buerger:ACC},
-where an active set solver is designed to solve the sequence of min-max problems explicitly online. In all 
-aforementioned papers and, to the authors' best knowledge, in published literature on algorithmic solutions to the RMPC 
-problem, the disturbance sets are assumed to be constant, i.e. independent of the system state and control inputs.
-Recent algorithmic advances allow us to treat polytopic disturbance sets which depend in an affine way on the system state
-and the control input. \cite{Schaich:2015} provide an algorithmic and analytical framework to
-embed affine state and input dependent disturbance constraints into the framework of the active set RMPC solver
-framework as proposed by~\cite{Buerger:2011}. Disturbance constraints varying with the state and input can be used
-to model multiplicative uncertainty as well as linearisation errors which will be shown in an example.
+input constraints, with model uncertainty in the form of bounded additive disturbances and/or multiplicative
+parameters. For the case of unknown additive disturbances, \citet{Scokaert:1998} propose a scenario-based
+approach to solve a sequence of min-max problems online, however the computational complexity of this approach
+grows exponentially with the length of the horizon. A parametrised algorithm was proposed
+by~\cite{Rakovic:2012} which reduces the RMPC problem to a single linear program to be solved online, but
+although this is a closed loop strategy the parametrisation is in general suboptimal. Explicit RMPC algorithms
+optimise the worst case predicted performance for each admissible model state offline and
+%exploit the structure of the solution using results
+use results from multi-parametric programming to parametrise the optimal control law as a piecewise affine function of the
+state \citep[e.g.][]{Bemporad:2003,Diehl:2004}. However, this requires extensive offline computation and
+becomes inefficient for a high-dimensional state space.
+An alternative approach that similarly exploits the piecewise affine structure of the solution, but with
+less redundancy, was proposed by~\cite{Buerger:2011} and extended in~\cite{Buerger:ACC}. In this work an active set
+solver is designed to solve a sequence of min-max problems explicitly online.
 
-After describing the considered control problem in section~\ref{sec:problem:statement} we summarise preliminary 
-results which are necessary to formulate the considered problem explicitly (section~\ref{sec:preliminaries}).
+In all of this work and, to the authors' best knowledge, in all of the published literature on algorithmic
+solutions to the RMPC problem, the disturbances are confined to sets that are assumed to be constant,
+i.e.~independent of the system state and control inputs. Recent algorithmic advances~\citep{Schaich:2015}
+make it possible to treat polytopic disturbance sets that depend in an affine manner on the system state and the control
+input. This provides an algorithmic and analytical framework which is used in the
+current paper to embed affine state and input dependent disturbance constraints into the framework of the
+active set RMPC solver framework proposed by~\cite{Buerger:2011}. Disturbances that belong to sets which depend
+on model states and inputs can account for multiplicative model uncertainty as well as linearisation
+errors, and the approach of this paper is therefore able to handle linearisation errors in RMPC non-conservatively.
+%, as will be shown in an example.
+
+After describing the control problem in Section~\ref{sec:problem:statement} we summarise preliminary 
+results which are necessary to formulate the considered problem explicitly (Section~\ref{sec:preliminaries}).
 Section~\ref{sec:gen:mpQP} discusses the recursive solution for equality constrained min-max recursions, one of 
-the essential parts of the active set solver, it is applied to the considered min-max problem in section~\ref{sec:applied:mpQP}
-assuming the active set of constraints is known. A line search to determine the active set of constraints is presented
-in section~\ref{sec:line:search}, the application of the proposed algorithm to an example system is presented in 
-section~\ref{sec:example}. Conclusions are given in section~\ref{sec:conclusion}.
+the essential parts of the active set solver, and this is applied to the min-max RMPC problem in Section~\ref{sec:applied:mpQP}
+for the case that the active set of constraints is known. A line search to determine the active set of constraints is presented
+in Section~\ref{sec:line:search}. The application of the proposed algorithm to an example problem is presented in 
+Section~\ref{sec:example} and conclusions are drawn in Section~\ref{sec:conclusion}.
 
 \section{Problem Statement}\label{sec:problem:statement}
-The set of systems to which a min-max robust receding horizon control scheme can be applied online 
-without approximating the solution is bounded by the system complexity. The way to solve min-max problems we 
-adopt here, is to use the structure of the solution and derive multi-parametric programs that can be solved 
-efficiently. In order to be able to obtain a closed form solution of the min-max program simple optimisation 
-formulations have to be available, in particular we consider linear constraints. In presence of state constraints 
-the algorithmic treatment of state constraints in min-max problems stagnated after it was introduced for fixed 
-polytopic disturbance sets by~\cite{Bertsekas:1971}. Recently~\cite{Schaich:2015} proposed an algorithm to compute the
-so called maximal robust positive invariant (MRPI) sets (see~\cite{blanchini:2007}) for linear systems subject to state 
-and input dependent disturbance constraints is presented. In this paper we develop the algorithm even further allowing 
-us to compute polytopic constraints necessary to satisfy state constraints robustly in this setup. We present a 
-robust receding horizon control scheme for
+We consider a computationally efficient method for solving online min-max receding horizon control problems
+that exploits the structure of multi-parametric programming solutions. Our approach determines the optimal
+feedback law without approximating the cost or the constraints of the problem, and without making restrictive
+assumptions on the parametrisation of control inputs.
+%This broadens the applicability of the approach, allowing for higher order models and longer
+%prediction horizons than 
 %
+%The high computational complexity of online min-max receding horizon control schemes generally requires either
+%that the solution is approximated or that their application is limited to problems involving simple system models and short horizons. Here we consider an
+%efficient method for solving min-max problems that exploits the structure of multi-parametric programming
+%solutions.
+%The set of systems to which a min-max robust receding horizon control scheme can be applied online 
+%without approximating the solution is bounded by the system complexity. The way to solve min-max problems we 
+%adopt here, is to use the structure of the solution to derive multi-parametric programs that can be solved
+%efficiently. In order to be able to obtain a closed form solution of the min-max program simple optimisation
+%formulations have to be
+%The algorithmic treatment of min-max problems
+%involving state constraints and disturbances constrained to lie in fixed polytopic disturbance sets was
+%introduced in~\cite{Bertsekas:1971}. Recently~\cite{Schaich:2015} proposed an algorithm to compute the so called maximal
+%robust positive invariant (MRPI) sets (see~\cite{blanchini:2007}) for linear systems subject to state and
+%input dependent disturbance constraints. In this paper we develop the algorithm further
+%to compute polytopic constraints necessary to satisfy state constraints robustly in this setup. We
+%present a robust receding horizon control scheme for
+%
+To make it possible to obtain a closed form solution of the min-max optimal control problem we assume a
+linear-quadratic problem formulation. Thus we assume the linear dynamic model 
 \begin{equation}\label{eq:system:equation}
@@
 where $A,B,D$ are real matrices of appropriate dimension, $x,  x^+\in\mathcal X\subseteq\mathbb R^n$ denote the state 
-and successor state respectively, $u\in\mathcal U=\{u:Fu\leq{\bf{1}}\}\subset\mathbb R^p$ the input and $w\in\mathcal W(x,u)
-\subset\mathbb R^q$ the disturbance with the state and input dependent disturbance set $\mathcal W(x,u)$. The disturbance 
-set $\mathcal W(x,u)$ is defined by
+and successor state respectively, $u\in\mathcal U=\{u:Fu\leq{\bf{1}}\}\subset\mathbb R^p$ is the control input
+and $w\in\mathcal W(x,u)\subset\mathbb R^q$ is an unknown disturbance input. The disturbance set $\mathcal
+W(x,u)$ is assumed to have a known dependence on the values of $x$ and $u$, according to
 %
@@
 %
-where $H(x,u)$ is an element-wise convex piecewise affine function. The min-max optimal control problem
-we will optimise is given by the $N$-stage min-max program
+where $H(x,u)$ is an elementwise convex, piecewise affine function. The control objective is to minimize the
+worst case value, over all future model uncertainty, of the cost
+\begin{equation}\label{eq:quadratic:cost}
+\sum_{k=0}^\infty \bigl( \|x_k\|_Q^2 + \|u_k\|_R^2 - \gamma^2 \|w_k\|^2 \bigr) ,
+\end{equation}
+where the subscript $k$ denotes the realisation of a variable at time $k$, $\|x\|_Q^2$ denotes the quadratic
+form $x^TQx$, $Q$ and $R$ are given positive definite
+matrices and $\gamma$ is a given scalar weight that controls the $l^2$-gain of the closed loop system from the
+disturbance sequence to the state and control sequences.
+
+Given a prediction horizon of $N$ steps over which the predicted control law is to be optimized, we define the
+min-max optimal control problem with $m$ stages to go as
 %
@@
 %
-where we enforce the stage wise state and input constraints $\mathcal Z_m$ in such a way that the terminal state,
-i.e. $x^+$ at $m=1$, is contained in the MRPI set $x^+\in\mathcal X^\infty$ for the closed-loop 
-system governed by a fixed state feedback controller $u=Kx$. The MRPI set $\mathcal X^\infty$ for this considered
-scenario is therefore given by
-%
-\begin{equation}\label{eq:definition:MRPI:set}
-	\mathcal X^\infty = \{x: (A+BK)x + Dw \in \mathcal X^\infty \forall w\in\mathcal W(x,Kx)\}.
-\end{equation}
-%
-subsequently the stage wise constraints $\mathcal Z_m$ are defined recursively as
+for $m=1,\ldots,N$, with $J_0^\ast(x) = \|x\|_{P_0}^2$.
+The stagewise  state and input constraints $\mathcal Z_m$ are defined recursively by
 %
@@
 	\label{eq:definition:state:stage:constraint}\\
-	\mathcal X_0 &= \mathcal X^\infty
 \end{align}
+with
+\begin{equation}
+	\mathcal X_0 = \mathcal X^\infty .
+\end{equation}
 \end{subequations}
+Thus the constraints $(x,u)\in\mathcal Z_m$ ensure that the terminal state, namely $x^+$ at $m=1$, is
+contained in $\mathcal{X}^\infty$.
+We define $\mathcal{X}^\infty$ as the maximal robust positive invariant (MRPI) set \citep{blanchini:2007}), for the closed-loop system governed by a fixed state feedback controller
+$u=Kx$, so that 
+%
+\begin{equation}\label{eq:definition:MRPI:set}
+	\mathcal X^\infty = \{x: (A+BK)x + Dw \in \mathcal X^\infty \forall w\in\mathcal W(x,Kx)\},
+\end{equation}
+%
+and we define $P_0$ so that $J_0^\ast(x)$ is the worst case value of the cost (\ref{eq:quadratic:cost}) under
+$u=Kx$ in the absence of constraints.
+Recently~\cite{Schaich:2015} proposed an algorithm to compute MRPI sets
+for linear systems subject to state and input dependent disturbance constraints. In this paper we combine this approach
+with the multistage multi-parametric programming method of~\cite{Buerger:ACC} to derive an efficient algorithmic
+solution to the online MPC optimization of (\ref{eq:the:problem}a-e).
 
-\section{Preliminaries}\label{sec:preliminaries}
-In this section we summarise preliminaries necessary to formulate the considered problem~\eqref{eq:the:problem}
-in a convenient way. The point-wise polytopic set defined by~\eqref{eq:PWA:def:disturbance} with a elementwise convex 
-piece-wise affine right-hand-side $H$ can be shown to lead to a polytopic MRPI set, see~\cite{Schaich:2015} for an 
-elaborate discussion. We summarise the result as we require it in
+\section{Controllable sets}\label{sec:preliminaries}
+In this section we summarise results on controllable sets that allow the constraints of the problem~\eqref{eq:the:problem} to be to formulated
+in a convenient way. The following result shows that the MRPI set (\ref{eq:definition:MRPI:set}) associated
+with the pointwise polytopic set~\eqref{eq:PWA:def:disturbance} is polytopic if $H$ is elementwise convex and
+piecewise affine. For a proof and detailed discussion of this result we refer the reader
+to~\cite{Schaich:2015}.
 %
 \begin{lem}\label{thm:MRPI:set:is:polytopic}
-Let $\mathcal X \subseteq \{x:\Gamma x\leq{\bf{1}}\wedge-\Gamma x\leq{\bf{1}}\}$ polyhedral, and the pair $(A+BK,\Gamma)$ be
+Let $\mathcal X \subseteq \{x:\Gamma x\leq{\bf{1}}\wedge-\Gamma x\leq{\bf{1}}\}$ be polyhedral, and the pair $(A+BK,\Gamma)$ be
 observable, furthermore let $\mathcal W(x,Kx)$ be defined as in~\eqref{eq:PWA:def:disturbance} with a elementwise convex piecewise
@@
 \begin{rem}\label{rem:vertex:representation}
-Notice that one essential assumption in Lemma~\ref{thm:MRPI:set:is:polytopic} is that $\mathcal W(x,u)$ is a polytope
+Note that an essential assumption in Lemma~\ref{thm:MRPI:set:is:polytopic} is that $\mathcal W(x,u)$ is a polytope
 for all finite $(x,u)$, i.e. it has a convex hull representation $\mathcal W(x,u) = \conv_k\{w_k(x,u)\}, k\in\{1,\dots,r\}$ where each 
-vertex~$w_k(x,u)$ is a piecewise affine function in $(x,u)$,i.e.
-\begin{equation}
-\Resize{
-	w_k(x,u) = \max\{W_{k,1}^x x + W_{k,1}^u u + w_{k,1},W_{k,2}^x x + W_{k,2}^u u + w_{k,2},\dots\}
-}
-\end{equation}
-where the maximisation is done elementwise.
+vertex, $w_k(x,u)$, is a piecewise affine function of $(x,u)$, i.e.
+\begin{multline}
+	w_k(x,u) = \max\{W_{k,1}^x x + W_{k,1}^u u + w_{k,1}, \\
+        W_{k,2}^x x + W_{k,2}^u u + w_{k,2},\dots\}
+\end{multline}
+where the maximisation is performed elementwise.
 \end{rem}
@@
 According to Lemma~\ref{thm:MRPI:set:is:polytopic} the MRPI set $\mathcal X^\infty$ is polytopic and has the 
-representation~\eqref{eq:halfspace:representation:MRPI}, the recursion~\eqref{eq:definition:mixed:stage:constraint}
-therefore defines $\mathcal Z_1$ as
+representation~\eqref{eq:halfspace:representation:MRPI}. Therefore the recursion~\eqref{eq:definition:mixed:stage:constraint}
+defines $\mathcal Z_1$ as
 \begin{equation}\label{eq:derivation:of:mpLP:stage:constraints}
-\Resize{
 \begin{aligned}
-	\mathcal Z_1 =& (\mathbb R^n\times\mathcal U)\cap\\
-	&\{(x,u):\Lambda_{0,i}(Ax+Bu+Dw)\leq\lambda_{0,i} \forall w\in\mathcal W(x,u),i\in\mathcal I_0\}\\
-	=&(\mathbb R^n\times\mathcal U)\cap\\
-	&\left\{\vphantom{\max_{w}}\right.
-	(x,u):\max_{w\in\mathcal W(x,u)}\Lambda_{0,i}(Ax+Bu+Dw)\leq\lambda_{0,i}\forall i\in\mathcal I_0
-	\left.\vphantom{\max_w}\right\}\\
-	=&(\mathbb R^n\times\mathcal U)\cap\\
-	&\left\{\vphantom{\max_{w}}\right.
-	\Lambda_{0,i}(Ax+Bu)+ \underbrace{\max_{j\in\{1,\dots,r\}}\Lambda_{0,i} Dw_j(x,u)}_{(I)}\leq\lambda_i\forall i\in\mathcal I_0
-	\left.\vphantom{\max_w}\right\}
+	\mathcal Z_1 =& (\mathbb R^n\times\mathcal U)\cap 
+\begin{aligned}[t] \Bigl\{(x,u): \Lambda_{0,i}(Ax&+Bu+Dw)\leq \lambda_{0,i} \\
+& \forall w\in\mathcal W(x,u),\, i\in\mathcal I_0 \Bigr\} \end{aligned}
+\\
+	=&\begin{aligned}[t] (\mathbb R^n & \times \mathcal U) \cap\Bigl\{ (x,u): \\
+& \max_{w\in\mathcal W(x,u)}\Lambda_{0,i}(Ax+Bu+Dw)\leq\lambda_{0,i},\, \forall i\in\mathcal I_0 \Bigr\} \end{aligned}
+\\
+	=&\begin{aligned}[t] & (\mathbb R^n \times\mathcal U)\cap \Bigl\{ (x,u): \\
+& \!\!\!\!\!\!
+\Lambda_{0,i}(Ax+Bu)+ \!\!\underbrace{\max_{j\in\{1,\dots,r\}}\Lambda_{0,i} Dw_j(x,u)}_{(i)}\leq\lambda_i, \, \forall i\in\mathcal I_0
+	\Bigr\} \end{aligned}
 \end{aligned}
-}
 \end{equation}
-The maximisation~$(I)$ in~\eqref{eq:derivation:of:mpLP:stage:constraints} is a multi-parametric
-linear program, its solution is piecewise affine. Therefore the set $\mathcal Z_1$ has a representation
-$\mathcal Z_1=\{(x,u):\Xi^x_{1,i}x+\Xi^u_{1,i}u\leq\xi_{1,i},i\in\mathcal J_1\}$, its projection~$\mathcal X_1$ 
-onto~$\mathbb R^n$ is therefore has the representation~$\mathcal X_1 = \{x:\Lambda_{1,i} x\leq\lambda_{1,i},i\in\mathcal I_1\}$.
+Since the maximisation $(i)$ in \eqref{eq:derivation:of:mpLP:stage:constraints} is a multi-parametric
+linear program, its solution is piecewise affine in $(x,u)$. 
+Therefore the set $\mathcal Z_1$ has a representation
+$\mathcal Z_1=\{(x,u):\Xi^x_{1,i}x+\Xi^u_{1,i}u\leq\xi_{1,i},i\in\mathcal J_1\}$. The projection~$\mathcal X_1$ 
+of $\mathcal Z_1$ onto~$\mathbb R^n$ is therefore has the representation~$\mathcal X_1 = \{x:\Lambda_{1,i} x\leq\lambda_{1,i},i\in\mathcal I_1\}$.
 From here the determination of $\mathcal Z_k$ and $\mathcal X_k$ follows recursively. We are now able to formulate 

### 2015-04-21 draft_v2.tex
edited sections 4 and 5

@@
 
-Numerous strategies have been proposed to solve RMPC problems for linear systems subject to linear state and
+Various strategies have been proposed to solve RMPC problems for linear systems subject to linear state and
 input constraints, with model uncertainty in the form of bounded additive disturbances and/or multiplicative
@@
 (see~\cite{bemporad02,Tondel:2003} for an extended discussion), as they are essential in the treatment 
-of the considered min-max program using an active set solver. Note that the notation in this section does 
-not refer to the notation in the preceding and proceeding sections.
-
+of the considered min-max program using an active set solver. 
+%Note that the notation in this section does not refer to the notation in the preceding and proceeding sections.
 Consider the primal equality-constrained concave mpQP
@@
 	V(\theta) = \left\{\begin{split}
-	\max_x & \;\frac{1}{2} x^T W x + c^Tx + d\\
-	\text{s.t.} &\; Hx  = f +S\theta
+	\max_{y} & \;\frac{1}{2} y^T W y + c^Ty + d\\
+	\text{s.t.} &\; Hy  = f +S\theta
 	\end{split}\right.
 \end{equation}
-for $W\preceq 0.$ The Lagrangian function associated with~\eqref{mpQP:primal} is
-\begin{equation}
-	L(x,\lambda,\theta)  = \frac{1}{2} x^T W x + c^Tx + d + \lambda^T(Hx - f - S\theta)
-\end{equation}
+%where  $y\in\mathbb{R}^{n_y}$ is the optimization variable, 
+where $W\preceq 0$, $c$, $d$, $H$, $f$, $S$ are constants and $\theta$ is a variable parameter. We wish to
+know how the solution of (\ref{mpQP:primal}) varies with $\theta$.  The Lagrangian function
+associated with~\eqref{mpQP:primal} is
+\[
+	L(y,\lambda,\theta)  = \frac{1}{2} y^T W y + c^Ty + d + \lambda^T(Hy - f - S\theta)
+\]
 and the dual problem is the unconstrained mpQP
@@
 	\begin{aligned}
-        W x + H^T\lambda & = -c \\
-        H x &= f + S\theta.
+        W y + H^T\lambda & = -c \\
+        H y &= f + S\theta.
 	\end{aligned}
@@
 
-\begin{thm}\label{thm:mpQP:solution}
+\begin{lem}\label{lem:mpQP:solution}
 The solution of~\eqref{kkt:conditions} has the representation
@@
 	\begin{split}
-		x &= M_\theta \theta + m\\
+		y &= M_\theta \theta + m\\
 		\lambda &= N_\theta \theta + N_\beta \beta + n
@@
 \end{equation}
-where $N_\beta\neq 0$ only if $H$ is rank deficient, in which case the rows
-of $N_\beta$ form a basis of the kernel of $H$, i.e. $H^TN_\beta=0$
-\end{thm}
+where $N_\beta\neq 0$ only if $H$ is not right invertible, in which case $H^TN_\beta=0$ and the columns
+of $N_\beta$ span ker$(H^T)$.
+\end{lem}
 %
-The matrices~$M_\theta$, $N_\theta$, $N_\beta$ as well as the vectors $m$ and $n$
-are constant, the variable $\beta$ is used to parametrise the solution in the null space of~\eqref{kkt:conditions}.
+The matrices $M_\theta$, $N_\theta$, $N_\beta$ and vectors $m$, $n$
+are constant and the variable $\beta$ is used to parametrise the solution in the null space
+of~\eqref{kkt:conditions}. We say (\ref{mpQP:primal}) is \textit{degenerate} if $N_\beta\neq 0$.
 %
 \begin{pf}
-There are two cases of rank deficient $H$: rank$(H)=n_x<n_\lambda$ and
-rank$(H)<\min\{n_x,n_\lambda\}$.
-Using the QR-decomposition (see e.g.~\cite{Nocedal:2006}) of $H=(Q_1,Q_2)\cdot(R^T,0)^T$ the solution 
+If $H$ is not right invertible, then we must have rank$(H)=n_y<n_\lambda$ or
+rank$(H)<\min\{n_y,n_\lambda\}$.
+For the case that rank$(H)=n_y$ (i.e.\ $H$ has full rank and $n_y<n_\lambda$), 
+using the QR-decomposition \citep[e.g.][]{Nocedal:2006} of $H=(Q_1,Q_2)\cdot(R^T,0)^T$ the solution 
 is given by $(m^T,n^T)^T = \Sigma (-c^T,f^T)^T$, $(M_\theta^T,N_\theta^T)^T = 
 \Sigma (0,S^T)^T$ and $N_\beta=Q_2$, where 
-\begin{equation}
+\[
 	\Sigma = \left(\begin{array}{cc}
@@
 	Q_1 R^{-T} & -Q_1R^{-T}WR^{-1}Q_1^T
-	\end{array}\right)
-\end{equation}
-in the case where the number of equality constraints is larger than the dimension of
-the primal variable, i.e. rank$(H)=n_x$. If rank$(H)<\min\{n_x,n_\lambda\}$, so that $R$ is
-not invertible, then
-\begin{equation}
+	\end{array}\right) .
+\]
+On the other hand if rank$(H)<\min\{n_y,n_\lambda\}$ (so that $H$ is rank deficient), then
+\[
 	\Sigma = \left(\begin{array}{cc}
@@
 	\end{array}\right)
-\end{equation}
+\]
 with $\Delta = (RW^{-1}R^T)^{-1}$. This concludes the proof.
@@
 However, substituting~\eqref{mpQP:solution} into the dual objective~\eqref{mpQP:dual} yields
-\begin{multline}
-    \mathcal D(\lambda(\theta,\beta),\theta) =  -\frac{1}{2}(N_\theta \theta + N_\beta \beta + n)^T H W^{-1}H^T 
-	(N_\theta \theta\\ + N_\beta \beta + n)
-	-(AW^{-1}c + 
-	f + S\theta)^T(N_\theta \theta + N_\beta \beta + n)\\ -\frac{1}{2}c^TW^{-1}c,
-\end{multline}
+\begin{align*}
+\mathcal D(&\lambda(\theta,\beta),\theta) = \\
+& {-\tfrac{1}{2}}(N_\theta \theta + N_\beta \beta + n)^T H W^{-1}H^T 
+	(N_\theta \theta + N_\beta \beta + n)\\
+& -(AW^{-1}c + 
+	f + S\theta)^T(N_\theta \theta + N_\beta \beta + n) -\tfrac{1}{2}c^TW^{-1}c,
+\end{align*}
 which is unbounded if
-\begin{equation}
+\[
 	(f^T+\theta^TS^T)N_\beta \neq 0
-\end{equation}
+\]
 and can be made arbitrarily small by the choice of $\beta$. Therefore we restrict $\theta$ to satisfy 
@@
 so that the dual mpQP has a unique solution
-and the choice of $\beta$ does not affect either the primal nor the dual cost and can be used for
-any purpose. For a general mpQP~\eqref{mpQP:compatability:assumption} is a restriction on the set
+and the choice of $\beta$ does not affect either the primal or the dual cost and can be used for
+any purpose. For a general mpQP, condition~\eqref{mpQP:compatability:assumption} is a restriction on the set
 of parameters for which~\eqref{mpQP:primal} has a solution of the form~\eqref{mpQP:solution}.
@@
 \begin{equation}\label{mpQP:cost:to:go}\begin{split}
-	V(\theta) = &\frac{1}{2}\theta^T M_\theta^T W M_\theta \theta + c^TM_\theta \theta
-\\&+ m^TWM_\theta+\frac{1}{2}m^T Wm + c^Tm\\
+	V(\theta) = &\frac{1}{2}\theta^T M_\theta^T W M_\theta \theta + c^TM_\theta \theta \\
+& + m^TWM_\theta+\frac{1}{2}m^T Wm + c^Tm\\
 =&\frac{1}{2} \theta^T W_\theta \theta + c^T_\theta \theta + d_\theta.
@@
 %
-Assume now that we want to solve
+Suppose now that we want to solve a problem that depends on the solution of~\eqref{mpQP:primal} and an
+additional parameter $\phi$:
 \begin{equation}\label{mpQP:second:stage} 
@@
 \end{equation}
-where the equality constraints include~\eqref{mpQP:compatability:assumption}. Since we know
-that the optimal cost-to-go $V(\theta)$ has the structure~\eqref{mpQP:cost:to:go}
-the problem~\eqref{mpQP:second:stage} reduces to a problem like~\eqref{mpQP:primal},
-which yields a solution like~\eqref{mpQP:solution}, i.e.
+where $\Phi$, $C$, $g$, $f$, $C$, $e$, $T$ are constants and
+the equality constraints include~\eqref{mpQP:compatability:assumption}. Since we know
+that the optimal cost-to-go $V(\theta)$ has the structure~\eqref{mpQP:cost:to:go},
+the problem~\eqref{mpQP:second:stage} reduces to a problem with the form of~\eqref{mpQP:primal},
+which yields a solution similar to~\eqref{mpQP:solution}, i.e.
 \begin{equation}
@@
 \end{equation}
-with the dual variable~$\eta$, as long as $\Phi+W_\theta\succ 0$. Finally we note 
-that~\eqref{mpQP:compatability:assumption} is only nontrivial if~$H$ is rank deficient and only 
+where $\eta$ is the dual variable, and $\Phi+W_\theta\succ 0$ has been assumed. Finally we note 
+that~\eqref{mpQP:compatability:assumption} is only nontrivial if~$H$ is not right invertible and only 
 introduces as many constraints on~$\theta$ as there are linearly
@@
 In the solution of recursive min-max programs such as~\eqref{eq:the:problem} we use the composition of
-the stage optimisers, i.e. we use $x(\theta(\phi)) = M_\theta K_\phi \phi + (M_\theta k + m)$.
-Notice that this composition of optimisers is again an affine function of the parameter, in particular
-we will exploit the fact that changing the parameter along a line will translate to a line in the optimiser
-space as long as no activations or deactivations in the constraints occur. We will revisit this fact
+the stage optimisers, i.e. we use $y(\theta(\phi)) = M_\theta K_\phi \phi + (M_\theta k + m)$.
+Notice that this composition of optimisers is again an affine function of the parameter $\phi$, in particular
+we will exploit the fact that parameter variations along lines translate to lines in the optimiser
+space as long as no activations or deactivations of constraints occur. We will revisit this fact
 when we perform a line search in order to update the active constraints.
@@
 %
-To use an active set solver for the problem:
+%To use an active set solver for the problem:
+First epx
 \begin{subequations}\label{eq:the:problem:reformulated}%
@@
 of~\eqref{eq:dist:cons}.
-With Lemma~\ref{thm:mpQP:solution} we obtain
+With Lemma~\ref{lem:mpQP:solution} we obtain
 \begin{equation}
@@
 The affine character of the solution of each sub-problem allows us to parametrise the entire trajectory
-with respect to parameters at stage~$m=N$, that is $x_N=\mathpzc x_0$ and $\beta_N$.
+with respect to parameters at stage~$m=N$, that is $x_N=\chi_0$ $x_N=\mathpzc x_0$ and $\beta_N$.
 
@@
 
-\section{Example}\label{sec:example}
-This section we present a numerical simulation in which the state-dependent uncertainty enters through an upper bound on the linearisation
-error for a nonlinear system. We consider an inverted pendulum described by $ml^2\ddot\varphi = mlg\sin\varphi+M$, where
-$m=0.1$\,kg is the mass, $l=0.3$\,m is the length of the pendulum, $g=9.81$\,m\,s$\mbox{}^{-2}$ is the gravitational
-constant and $M$ is the direct torque input. Discretisation using Euler backward finite differences 
-at $f = 20$\,Hz yields
-\begin{equation}
-  \begin{split}
-    x_1[k+1] &= x_1[k] + \frac{1}{f} x_2[k]\\
-    x_2[k+1] &= \frac{g}{fl} \sin(x_1[k]) + x_2[k] + \frac{1}{fml^2}u[k]
-  \end{split}
-\end{equation}
-where $x_1[k] = \varphi(t_0+k/f),x_2[k] = \dot\varphi(t_0+k/f)$ and $u[k] = M(t_0+k/f)$.
-The nonlinearity is given by the sine function, and we can explicitly state the 
-linearisation error as $e(x_1)=\frac{g}{fl}(\sin x_1 - x_1)$. Since the linearisation
-only approximates the nonlinear dynamics around the equilibrium we can choose a closed interval 
-$0\in D\subset\mathbb R$ and maximise the upper bound 
-\begin{equation}
-  \Delta e = \max_{x_1\in D}\abs{\frac{de}{dx_1}} = \frac{g}{fl}\max_{x_1\in D}\abs{\cos x_1-1}.
-\end{equation}
-This results in the linear system
-\begin{equation}
-  x^+ = \underbrace{\left(\begin{array}{cc}
-  1 & f^{-1}\\ g(fl)^{-1} & 1
-  \end{array}\right)}_A x + \underbrace{\left(\begin{array}{c} 0 \\(ml^2f)^{-1} \end{array}\right)}_B u
-  +\left(\begin{array}{c}w_1\\ w_2\end{array}\right)
-\end{equation}
-with $\abs{w_1}\leq w_{1,\max}$ and $\abs{w_2}\leq\max\{w_{2,\max},\Delta e \abs{x_1}\}$.
-We also introduce the input constraint $\abs{u}\leq3$\,N\,m and use the interval $D = [-\frac{3\pi}{4},
-\frac{3\pi}{4}]$ and a horizon of $N=7$ to obtain the sequence of state constraints $\mathcal X_m$
-depicted in Figure~\ref{fig:numerical:example}. The line search starting at the origin and
-exploring towards $\mathpzc x_e=(-6,50)$ produces the optimal trajectories at the active-set switches
-which are illustrated in blue. In pink a warm-started line search terminates on the boundary of the
-feasible set before reaching the (infeasible) state $\mathpzc x_e=(0,30)$.
+\input{example.tex}
 

### 2015-04-21 example.tex
Split off example.

--- 2015-03-26 draft.tex
@@
-%===============================================================================
-% $Id: ifacconf.tex 19 2011-10-27 09:32:13Z jpuente $  
-% Template for IFAC meeting papers
-% Copyright (c) 2007-2008 International Federation of Automatic Control
-%===============================================================================
-\documentclass{ifacconf}
-
-\usepackage{graphicx}      % include this line if your document contains figures
-\usepackage{natbib}        % required for bibliography
-\usepackage{epsfig}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{mathrsfs}
-
-\usepackage{todonotes}
-\newcommand{\NOTE}[1]{\todo[inline]{#1}}
-
-\newcommand*{\Resize}[1]{\resizebox{\columnwidth}{!}{$#1$}}
-
-\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
-
-\providecommand{\norm}[1]{\left\|#1\right\|}
-\providecommand{\abs}[1]{\left|#1\right|}
-\providecommand{\conv}{\text{conv}}
-
-\usepackage{xcolor}
-\def\edit{\textcolor{blue}}
-\allowdisplaybreaks[4]
-
-%===============================================================================
-\begin{document}
-\begin{frontmatter}
-
-% predefined environments
-%\begin{thm} ... \end{thm}		% Theorem
-%\begin{lem} ... \end{lem}		% Lemma
-%\begin{claim} ... \end{claim}	% Claim
-%\begin{conj} ... \end{conj}	% Conjecture
-%\begin{cor} ... \end{cor}		% Corollary
-%\begin{fact} ... \end{fact}	% Fact
-%\begin{hypo} ... \end{hypo}	% Hypothesis
-%\begin{prop} ... \end{prop}	% Proposition
-%\begin{crit} ... \end{crit}	% Criterion
-%\begin{rem} ... \end{rem}    % Remark
-%\begin{pf} ... \end{pf}      % Proof
-%\begin{ack} ... end{ack}     % Acknowledgement
-
-\title{Robust receding horizon control for linear systems with state dependent disturbance}
-
-\thanks[footnoteinfo]{Supported by the Martin Senior Scholarship of Worcester College, Oxford.}
-
-\author[Oxford]{Rainer M. Schaich\thanksref{footnoteinfo}} 
-\author[Oxford]{Mark Cannon}
-
-\address[Oxford]{Department of Engineering Science, University of Oxford, OX1 3PJ, UK. (e-mail: 
-rainer.schaich@eng.ox.ac.uk, mark.cannon@eng.ox.ac.uk).}
-
-\begin{abstract}                % Abstract of not more than 250 words.
-
-\end{abstract}
-
-\begin{keyword}
--
-\end{keyword}
-
-\end{frontmatter}
-%===============================================================================
-
-\section{Introduction}\label{sec:intro}
-Robust model predictive control (RMPC) algorithms compute a control law optimising a performance
-criterion subject to state and control constraints for a perturbed system, for all possible realisations of the
-perturbation. \cite{Witsenhausen:1968} proposes to formulate the RMPC problem as a game in which the adversary 
-tries to maximise the effect of the uncertainty on the cost and the controller chooses its strategy to minimise 
-the cost for the worst case system, this formulation is widely accepted, see e.g.~\cite{Bemporad:1999,Bemporad:2003,Lee:1997}.
-The worst case system can either be considered to be open-loop, i.e. the controller chooses its strategy for the 
-whole horizon before the adversary decides its strategy, or closed-loop, i.e. at each stage along the horizon 
-the controller and the adversary play the game for only that stage given the outcome of the previous stage.
-Theoretical properties of these controllers are well understood, see e.g.~\cite{Mayne:2000}. However, the
-numerical computation of robust model predictive controllers still poses a challenge and only few tractable 
-solutions have been proposed.
-
-Numerous strategies have been proposed to solve RMPC problems for linear systems subject to linear state and
-input constraints and linearly constrained additive uncertainty.
-\NOTE{Do we need to constrain ourselves to additive here? In the literature there are algorithms that cope with
-multiplicative just as well..?!}
-\cite{Scokaert:1998} propose a scenario-based approach to solve the sequence of min-max problems, however the
-complexity grows exponentially with the length of the horizon. A parametrised algorithm was proposed by~\cite{Rakovic:2012}
-which can be used to reduce the RMPC problem to a single linear program that can be solved online, bit this 
-parametrisation is in general suboptimal. Explicit RMPC algorithms solve the min-max problems offline and exploit 
-the structure of the solution using results from multi-parametric programming to parametrise the optimal feedback as 
-piecewise affine functions of the state, see e.g.~\cite{Bemporad:2003,Diehl:2004}. However, this requires extensive offline
-computation and becomes inefficient for a high dimensional state space. Another approach exploiting the structure
-of the solution in the same way but with less redundancy was proposed by~\cite{Buerger:2011} and extended in~\cite{Buerger:ACC},
-where an active set solver is designed to solve the sequence of min-max problems explicitly online. In all 
-aforementioned papers and, to the authors' best knowledge, in published literature on algorithmic solutions to the RMPC 
-problem, the disturbance sets are assumed to be constant, i.e. independent of the system state and control inputs.
-Recent algorithmic advances allow us to treat polytopic disturbance sets which depend in an affine way on the system state
-and the control input. \cite{Schaich:2015} provide an algorithmic and analytical framework to
-embed affine state and input dependent disturbance constraints into the framework of the active set RMPC solver
-framework as proposed by~\cite{Buerger:2011}. Disturbance constraints varying with the state and input can be used
-to model multiplicative uncertainty as well as linearisation errors which will be shown in an example.
-
-After describing the considered control problem in section~\ref{sec:problem:statement} we summarise preliminary 
-results which are necessary to formulate the considered problem explicitly (section~\ref{sec:preliminaries}).
-Section~\ref{sec:gen:mpQP} discusses the recursive solution for equality constrained min-max recursions, one of 
-the essential parts of the active set solver, it is applied to the considered min-max problem in section~\ref{sec:applied:mpQP}
-assuming the active set of constraints is known. A line search to determine the active set of constraints is presented
-in section~\ref{sec:line:search}, the application of the proposed algorithm to an example system is presented in 
-section~\ref{sec:example}. Conclusions are given in section~\ref{sec:conclusion}.
-
-\section{Problem Statement}\label{sec:problem:statement}
-The set of systems to which a min-max robust receding horizon control scheme can be applied online 
-without approximating the solution is bounded by the system complexity. The way to solve min-max problems we 
-adopt here, is to use the structure of the solution and derive multi-parametric programs that can be solved 
-efficiently. In order to be able to obtain a closed form solution of the min-max program simple optimisation 
-formulations have to be available, in particular we consider linear constraints. In presence of state constraints 
-the algorithmic treatment of state constraints in min-max problems stagnated after it was introduced for fixed 
-polytopic disturbance sets by~\cite{Bertsekas:1971}. Recently~\cite{Schaich:2015} proposed an algorithm to compute the
-so called maximal robust positive invariant (MRPI) sets (see~\cite{blanchini:2007}) for linear systems subject to state 
-and input dependent disturbance constraints is presented. In this paper we develop the algorithm even further allowing 
-us to compute polytopic constraints necessary to satisfy state constraints robustly in this setup. We present a 
-robust receding horizon control scheme for
-%
-\begin{equation}\label{eq:system:equation}
-	x^+ = A x + B u + D w,
-\end{equation}
-%
-where $A,B,D$ are real matrices of appropriate dimension, $x, x^+\in\mathcal X\subseteq\mathbb R^n$ denote the state 
-and successor state respectively, $u\in\mathcal U=\{u:Fu\leq{\bf{1}}\}\subset\mathbb R^p$ the input and $w\in\mathcal W(x,u)
-\subset\mathbb R^q$ the disturbance with the state and input dependent disturbance set $\mathcal W(x,u)$. The disturbance 
-set $\mathcal W(x,u)$ is defined by
-%
-\begin{equation}\label{eq:PWA:def:disturbance}
-	\mathcal W(x,u) = \{w: Gw \leq H(x,u)\},
-\end{equation}
-%
-where $H(x,u)$ is an element-wise convex piecewise affine function. The min-max optimal control problem
-we will optimise is given by the $N$-stage min-max program
-%
-\begin{subequations}\label{eq:the:problem}%
-\begin{equation}
-	J_{m}^\ast(x) = \min_u \max_{w,x^+} \tfrac{1}{2}\bigl(\norm{x}_Q^2+\norm{u}_R^2-\gamma^2
-    \norm{w}^2\bigr) + J_{m-1}^\ast(x^+)
-\end{equation}
-subject to
-\begin{gather}
-	x^+ = A x + B u + D w\\
-	u\in\mathcal U \\
-	w\in\mathcal W(x,u) \\
-	(x,u)\in\mathcal Z_m
-\end{gather}
-\end{subequations}
-%
-where we enforce the stage wise state and input constraints $\mathcal Z_m$ in such a way that the terminal state,
-i.e. $x^+$ at $m=1$, is contained in the MRPI set $x^+\in\mathcal X^\infty$ for the closed-loop 
-system governed by a fixed state feedback controller $u=Kx$. The MRPI set $\mathcal X^\infty$ for this considered
-scenario is therefore given by
-%
-\begin{equation}\label{eq:definition:MRPI:set}
-	\mathcal X^\infty = \{x: (A+BK)x + Dw \in \mathcal X^\infty \forall w\in\mathcal W(x,Kx)\}.
-\end{equation}
-%
-subsequently the stage wise constraints $\mathcal Z_m$ are defined recursively as
-%
-\begin{subequations}\label{eq:definition:stage:constraints}
-\begin{align}
-	\mathcal Z_m &= \{(x,u)\,: u\in\mathcal U \nonumber\\
-	&\quad\ \wedge \; A x + Bu + Dw\in\mathcal X_{m-1}\; \forall\, w\in\mathcal W(x,u)\} 
-	\label{eq:definition:mixed:stage:constraint}\\
-	\mathcal X_m &= \{x : \exists\, u\in\mathcal U, (x,u)\in\mathcal Z_m\}
-	\label{eq:definition:state:stage:constraint}\\
-	\mathcal X_0 &= \mathcal X^\infty
-\end{align}
-\end{subequations}
-
-\section{Preliminaries}\label{sec:preliminaries}
-In this section we summarise preliminaries necessary to formulate the considered problem~\eqref{eq:the:problem}
-in a convenient way. The point-wise polytopic set defined by~\eqref{eq:PWA:def:disturbance} with a elementwise convex 
-piece-wise affine right-hand-side $H$ can be shown to lead to a polytopic MRPI set, see~\cite{Schaich:2015} for an 
-elaborate discussion. We summarise the result as we require it in
-%
-\begin{lem}\label{thm:MRPI:set:is:polytopic}
-Let $\mathcal X \subseteq \{x:\Gamma x\leq{\bf{1}}\wedge-\Gamma x\leq{\bf{1}}\}$ polyhedral, and the pair $(A+BK,\Gamma)$ be
-observable, furthermore let $\mathcal W(x,Kx)$ be defined as in~\eqref{eq:PWA:def:disturbance} with a elementwise convex piecewise
-affine function $H(x,Kx)$ which is bounded for all finite $x$. Then the MRPI set $\mathcal X^\infty$ is a polytope, i.e.
-it has the representation 
-\begin{equation}\label{eq:halfspace:representation:MRPI}
-	\mathcal X^\infty=\{x:\Lambda_i x\leq \lambda_i, \forall\, i\in\mathcal I^\infty\}.
-\end{equation}
-\end{lem}
-%
-We need to emphasise the following 
-\begin{rem}\label{rem:vertex:representation}
-Notice that one essential assumption in Lemma~\ref{thm:MRPI:set:is:polytopic} is that $\mathcal W(x,u)$ is a polytope
-for all finite $(x,u)$, i.e. it has a convex hull representation $\mathcal W(x,u) = \conv_k\{w_k(x,u)\}, k\in\{1,\dots,r\}$ where each 
-vertex~$w_k(x,u)$ is a piecewise affine function in $(x,u)$,i.e.
-\begin{equation}
-\Resize{
-	w_k(x,u) = \max\{W_{k,1}^x x + W_{k,1}^u u + w_{k,1},W_{k,2}^x x + W_{k,2}^u u + w_{k,2},\dots\}
-}
-\end{equation}
-where the maximisation is done elementwise.
-\end{rem}
-%
-We now derive the representation of $\mathcal Z_m$ and $\mathcal X_m$ as defined in~\eqref{eq:definition:stage:constraints}.
-According to Lemma~\ref{thm:MRPI:set:is:polytopic} the MRPI set $\mathcal X^\infty$ is polytopic and has the 
-representation~\eqref{eq:halfspace:representation:MRPI}, the recursion~\eqref{eq:definition:mixed:stage:constraint}
-therefore defines $\mathcal Z_1$ as
-\begin{equation}\label{eq:derivation:of:mpLP:stage:constraints}
-\Resize{
-\begin{aligned}
-	\mathcal Z_1 =& (\mathbb R^n\times\mathcal U)\cap\\
-	&\{(x,u):\Lambda_{0,i}(Ax+Bu+Dw)\leq\lambda_{0,i} \forall w\in\mathcal W(x,u),i\in\mathcal I_0\}\\
-	=&(\mathbb R^n\times\mathcal U)\cap\\
-	&\left\{\vphantom{\max_{w}}\right.
-	(x,u):\max_{w\in\mathcal W(x,u)}\Lambda_{0,i}(Ax+Bu+Dw)\leq\lambda_{0,i}\forall i\in\mathcal I_0
-	\left.\vphantom{\max_w}\right\}\\
-	=&(\mathbb R^n\times\mathcal U)\cap\\
-	&\left\{\vphantom{\max_{w}}\right.
-	\Lambda_{0,i}(Ax+Bu)+ \underbrace{\max_{j\in\{1,\dots,r\}}\Lambda_{0,i} Dw_j(x,u)}_{(I)}\leq\lambda_i\forall i\in\mathcal I_0
-	\left.\vphantom{\max_w}\right\}
-\end{aligned}
-}
-\end{equation}
-The maximisation~$(I)$ in~\eqref{eq:derivation:of:mpLP:stage:constraints} is a multi-parametric
-linear program, its solution is piecewise affine. Therefore the set $\mathcal Z_1$ has a representation
-$\mathcal Z_1=\{(x,u):\Xi^x_{1,i}x+\Xi^u_{1,i}u\leq\xi_{1,i},i\in\mathcal J_1\}$, its projection~$\mathcal X_1$ 
-onto~$\mathbb R^n$ is therefore has the representation~$\mathcal X_1 = \{x:\Lambda_{1,i} x\leq\lambda_{1,i},i\in\mathcal I_1\}$.
-From here the determination of $\mathcal Z_k$ and $\mathcal X_k$ follows recursively. We are now able to formulate 
-all constraints in~\eqref{eq:the:problem} as inequalities. In the next section we discuss a method of solving
-min-max programs such as~\eqref{eq:the:problem} efficiently.
-
-\section{Solving equality constrained multi-parametric quadratic programs}\label{sec:gen:mpQP}
-In this section we discuss equality constraint multi-parametric quadratic programs (mpQP) 
-(see~\cite{bemporad02,Tondel:2003} for an extended discussion), as they are essential in the treatment 
-of the considered min-max program using an active set solver. Note that the notation in this section does 
-not refer to the notation in the preceding and proceeding sections.
-
-Consider the primal equality-constrained concave mpQP
-\begin{equation}\label{mpQP:primal}
-	V(\theta) = \left\{\begin{split}
-	\max_x & \;\frac{1}{2} x^T W x + c^Tx + d\\
-	\text{s.t.} &\; Hx  = f +S\theta
-	\end{split}\right.
-\end{equation}
-for $W\preceq 0.$ The Lagrangian function associated with~\eqref{mpQP:primal} is
-\begin{equation}
-	L(x,\lambda,\theta)  = \frac{1}{2} x^T W x + c^Tx + d + \lambda^T(Hx - f - S\theta)
-\end{equation}
-and the dual problem is the unconstrained mpQP
-\begin{equation}\label{mpQP:dual}\begin{split}
-	\min_\lambda &\; \mathcal D(\lambda,\theta)= \min_\lambda-\frac{1}{2}\lambda^T H W^{-1}H^T \lambda 
-	-(HW^{-1}c\\ &+ f + S\theta)^T\lambda
-	-\frac{1}{2}c^TW^{-1}c +d
-\end{split}\end{equation}
-To solve~\eqref{mpQP:primal} we consider the first order optimality conditions, see e.g.~\cite{Fletcher:2000}:
-\begin{equation}\label{kkt:conditions}
-	\begin{aligned}
-        W x + H^T\lambda & = -c \\
-        H x &= f + S\theta.
-	\end{aligned}
-\end{equation}
-
-\begin{thm}\label{thm:mpQP:solution}
-The solution of~\eqref{kkt:conditions} has the representation
-\begin{equation}\label{mpQP:solution}
-	\begin{split}
-		x &= M_\theta \theta + m\\
-		\lambda &= N_\theta \theta + N_\beta \beta + n
-	\end{split}
-\end{equation}
-where $N_\beta\neq 0$ only if $H$ is rank deficient, in which case the rows
-of $N_\beta$ form a basis of the kernel of $H$, i.e. $H^TN_\beta=0$
-\end{thm}
-%
-The matrices~$M_\theta$, $N_\theta$, $N_\beta$ as well as the vectors $m$ and $n$
-are constant, the variable $\beta$ is used to parametrise the solution in the null space of~\eqref{kkt:conditions}.
-%
-\begin{pf}
-There are two cases of rank deficient $H$: rank$(H)=n_x<n_\lambda$ and
-rank$(H)<\min\{n_x,n_\lambda\}$.
-Using the QR-decomposition (see e.g.~\cite{Nocedal:2006}) of $H=(Q_1,Q_2)\cdot(R^T,0)^T$ the solution 
-is given by $(m^T,n^T)^T = \Sigma (-c^T,f^T)^T$, $(M_\theta^T,N_\theta^T)^T = 
-\Sigma (0,S^T)^T$ and $N_\beta=Q_2$, where 
-\begin{equation}
-	\Sigma = \left(\begin{array}{cc}
-	0 & R^{-1}Q_1^T \\
-	Q_1 R^{-T} & -Q_1R^{-T}WR^{-1}Q_1^T
-	\end{array}\right)
-\end{equation}
-in the case where the number of equality constraints is larger than the dimension of
-the primal variable, i.e. rank$(H)=n_x$. If rank$(H)<\min\{n_x,n_\lambda\}$, so that $R$ is
-not invertible, then
-\begin{equation}
-	\Sigma = \left(\begin{array}{cc}
-	W^{-1}-W^{-1}R^T\Delta RW^{-1} & W^{-1}R^{T}\Delta Q_1^{T}\\
-	Q_1\Delta R W^{-1} & -Q_1\Delta Q_1^T
-	\end{array}\right)
-\end{equation}
-with $\Delta = (RW^{-1}R^T)^{-1}$. This concludes the proof.
-\end{pf}
-%
-Since the degeneracy variable $\beta$ does not appear in the
-primal optimiser, it does not affect the primal objective value of~\eqref{mpQP:primal}.
-However, substituting~\eqref{mpQP:solution} into the dual objective~\eqref{mpQP:dual} yields
-\begin{multline}
-    \mathcal D(\lambda(\theta,\beta),\theta) =  -\frac{1}{2}(N_\theta \theta + N_\beta \beta + n)^T H W^{-1}H^T 
-	(N_\theta \theta\\ + N_\beta \beta + n)
-	-(AW^{-1}c + 
-	f + S\theta)^T(N_\theta \theta + N_\beta \beta + n)\\ -\frac{1}{2}c^TW^{-1}c,
-\end{multline}
-which is unbounded if
-\begin{equation}
-	(f^T+\theta^TS^T)N_\beta \neq 0
-\end{equation}
-and can be made arbitrarily small by the choice of $\beta$. Therefore we restrict $\theta$ to satisfy 
-\begin{equation}\label{mpQP:compatability:assumption}
-	N_\beta^Tf = -N_\beta^TS\theta,
-\end{equation} 
-so that the dual mpQP has a unique solution
-and the choice of $\beta$ does not affect either the primal nor the dual cost and can be used for
-any purpose. For a general mpQP~\eqref{mpQP:compatability:assumption} is a restriction on the set
-of parameters for which~\eqref{mpQP:primal} has a solution of the form~\eqref{mpQP:solution}.
-In our multi-stage min-max setup, the parameter is the optimiser of a subsequent optimisation
-problem and can be ensured to satisfy~\eqref{mpQP:compatability:assumption} by the so called 
-compatibility constraint. The optimal objective of~\eqref{mpQP:primal} is given by
-\begin{equation}\label{mpQP:cost:to:go}\begin{split}
-	V(\theta) = &\frac{1}{2}\theta^T M_\theta^T W M_\theta \theta + c^TM_\theta \theta
-\\&+ m^TWM_\theta+\frac{1}{2}m^T Wm + c^Tm\\
-=&\frac{1}{2} \theta^T W_\theta \theta + c^T_\theta \theta + d_\theta.
-\end{split}\end{equation}
-%
-Assume now that we want to solve
-\begin{equation}\label{mpQP:second:stage}
-	J(\phi) = \left\{\begin{array}{rl}
-	\min_\theta & \frac{1}{2}\theta^T\Phi\theta + g^T\theta + f + V(\theta)\\
-	\text{s.t.} & C\theta = e+T\phi
-	\end{array}\right.
-\end{equation}
-where the equality constraints include~\eqref{mpQP:compatability:assumption}. Since we know
-that the optimal cost-to-go $V(\theta)$ has the structure~\eqref{mpQP:cost:to:go}
-the problem~\eqref{mpQP:second:stage} reduces to a problem like~\eqref{mpQP:primal},
-which yields a solution like~\eqref{mpQP:solution}, i.e.
-\begin{equation}
-\begin{split}
-	\theta &= K_\phi \phi + k\\
-	\eta &= L_\phi \phi + L_{\hat\beta} \hat\beta + l
-\end{split}
-\end{equation}
-with the dual variable~$\eta$, as long as $\Phi+W_\theta\succ 0$. Finally we note 
-that~\eqref{mpQP:compatability:assumption} is only nontrivial if~$H$ is rank deficient and only 
-introduces as many constraints on~$\theta$ as there are linearly
-dependent rows in~$H$.
-
-In the solution of recursive min-max programs such as~\eqref{eq:the:problem} we use the composition of
-the stage optimisers, i.e. we use $x(\theta(\phi)) = M_\theta K_\phi \phi + (M_\theta k + m)$.
-Notice that this composition of optimisers is again an affine function of the parameter, in particular
-we will exploit the fact that changing the parameter along a line will translate to a line in the optimiser
-space as long as no activations or deactivations in the constraints occur. We will revisit this fact
-when we perform a line search in order to update the active constraints.
-
-\section{Solving min-max quadratic programs as multi-parametric quadratic programs}\label{sec:applied:mpQP}
-In this section we apply the results derived in section~\ref{sec:gen:mpQP} to
-the considered min-max robust control problem~\eqref{eq:the:problem}. We 
-define a recursion and assume the active set is known to obtain a closed solution for~\eqref{eq:the:problem}.
-%
-To use an active set solver for the problem:
-\begin{subequations}\label{eq:the:problem:reformulated}%
-\begin{equation}
-	J_{m}^\ast(x) = \min_u \max_{w,x^+} \tfrac{1}{2}\bigl(\norm{x}_Q^2+\norm{u}_R^2-\gamma^2
-    \norm{w}^2\bigr) + J_{m-1}^\ast(x^+)
-\end{equation}
-subject to
-\begin{gather}
-	x^+ = A x + B u + D w
-\\
-\label{eq:dist:cons}
-	G w \leq  H(x,u)
-\\
-\label{eq:state:constraints}
-	\Xi^x_m x + \Xi^u_m u \leq \xi_m
-\\
-	\hat C_m x^+ = - {\bf{1}}
-\\
-	C_m^x x + C_m^u u  = {\bf{1}}
-\end{gather}
-\end{subequations}
-with~$J_0^\ast(x^+) = \frac{1}{2}\norm{x^+}_P^2$ and $m=1,\dots,N$. Notice that explicitly using
-$u\in\mathcal U$ is no longer necessary as satisfaction of the input constraints is intrinsic
-if $(\cdot,u)\in\mathcal Z_m$.
-We split the sequence of  min-max problems into a sequence of multi-parametric 
-quadratic programs. Starting with the maximisation at stage $m=1$ and using a backward sweep approach (see e.g.~\cite{Bryson:1975}), 
-we obtain
-\begin{equation}
-	\hat J_m^\ast(x,u) = \left\{\begin{split}
-    \max_{w,x^+} & -\frac{\gamma^2}{2}\norm{w}^2 + J_{m-1}^\ast(x^+)\\
-    \text{s.t.} & \begin{array}{rcl}
-    Gw & \leq & H(x,u)\\
-    x^+ & = & Ax + Bu + Dw\\
-    \hat C_m x^+ &=& -{\bf{1}}
-    \end{array}
-    \end{split}\right.
-\end{equation}
-and
-\begin{equation}
-	J_m^\ast(x) = \left\{\begin{split}
-    \min_{u} & \frac{1}{2}\left(\norm{x}^2_Q + \norm{u}_R^2\right) + \hat J_m^\ast(x,u)\\
-    \text{s.t.} & \begin{array}{ccccl}
-    \Xi^x_m x &+& \Xi^u_m u &\leq &\xi_m\\
-    C_m^x x &+ & C^u_m u & = & {\bf{1}}
-    \end{array}
-    \end{split}
-    \right.
-\end{equation}
-Suppose the active set is given, i.e.~it is known which inequality constraints hold with equality. 
-For notational convenience we denote active inequalities with $(\cdot)^\prime$, e.g.  $(\Xi^x_m)^\prime x + (\Xi^u_m)^\prime u = \xi_m^\prime$. 
-Since $J^\ast_0(x^+) = \frac{1}{2}\norm{x^+}_{P_0}^2$ is a given function, compatibility constraints are not necessary at 
-stage $m=1$ and the maximisation problem is given by:
-\begin{equation}
-	\hat J_1^\ast(x,u) = \left\{\begin{split}
-	\max_{w,x^+} & -\frac{\gamma^2}{2}\norm{w}^2 + J_{0}^\ast(x^+)\\
-	\text{s.t.} & 
-	\underbrace{\left(\begin{array}{cc}
-	G^\prime & 0 \\ -D & I
-	\end{array}\right)}_{\bar H}
-	\left(\begin{array}{c}w\\ x^+\end{array}\right)
-	\\&= \underbrace{\left(\begin{array}{cc}W_x^\prime & W_u^\prime \\ A & B\end{array}\right)}_{
-	\bar S
-	}
-	\left(\begin{array}{c}x \\ u \end{array}\right) + \underbrace{\left(\begin{array}{c}
-	w_c^\prime \\ 0\end{array}\right)}_{\bar f}
-	\end{split}\right.
-\end{equation}
-with $W_x^\prime, W_u^\prime$ and $w_c^\prime$ denoting the active rows of the right hand side 
-of~\eqref{eq:dist:cons}.
-With Lemma~\ref{thm:mpQP:solution} we obtain
-\begin{equation}
-      \left(\begin{array}{c}
-      w^\ast \\
-      x^{+,\ast} \\
-      \eta^\ast \\
-      \lambda^\ast
-      \end{array}\right) = \left(\begin{array}{c}M^w_z\\ M^{x^+}_z \\ N^{\eta}_z \\ N^{\lambda}_z
-      \end{array}\right)\underbrace{\left(\begin{array}{c}x\\ u\end{array}\right)}_z + 
-      \left(\begin{array}{c}0\\ 0 \\ N^{\eta}_{\hat\beta} \\ N^{\lambda}_{\hat\beta}
-      \end{array}\right)\hat\beta + \left(\begin{array}{c}m^w\\ m^{x^+} \\ n^{\eta} \\ n^{\lambda}
-      \end{array}\right)
-\end{equation}
-where $\eta^\ast$ denotes the dual variable to the active inequality constraints and hence must
-be non-negative, i.e.~$\eta^\ast\geq0$. Notice that we omitted stage indices to avoid overloaded notation.
-The cost-to-go for the minimisation problem at stage $m=1$ is
-\begin{equation}
-	\hat J_1^\ast(z) = \frac{1}{2}z^T
-    \hat Q_1 z + c_1 z + d_1
-\end{equation}
-and the compatibility constraint is given by
-\begin{equation}\label{prototype:compatibility:conditions}
-	N_{\hat\beta}^T(\bar S z + \bar f) = 0,
-\end{equation}
-i.e.\ $C_1^x$ and $C_1^u$ are given as a row wise normalised version of~\eqref{prototype:compatibility:conditions}.
-Hence the minimisation problem at $m=1$ becomes
-\begin{equation}
-	J_1^\ast(x) = \left\{\begin{split}
-	\min_{u} & \frac{1}{2}\left(\norm{x}^2_Q + \norm{u}_R^2\right) + \hat J_{1}^\ast(x,u)\\
-    \text{s.t.} & 
-    \underbrace{\left(\begin{array}{c}
-    (\Xi_1^u)^\prime \\ C_1^u
-    \end{array}\right)}_{\bar C}
-    u
-    = \underbrace{\left(\begin{array}{c}-(\Xi^x_1)^\prime \\ -C_1^x\end{array}\right)}_{
-    \bar T
-    }x + 
-    \underbrace{\left(\begin{array}{c}\xi_1^\prime\\  {\bf{1}} \end{array}\right)}_{\bar e}
-    \end{split}\right.
-\end{equation}
-and its solution is given by
-\begin{equation}
-	\left(\begin{array}{c}
-	u^\ast \\
-	\nu^\ast \\
-	\hat\zeta^\ast
-	\end{array}\right) = \left(\begin{array}{c}K^u_x\\ O^{\nu}_x \\ O^{\hat\zeta}_x
-	\end{array}\right)x + 
-	\left(\begin{array}{c}0\\ O^{\nu}_\beta \\ O^{\hat\zeta}_{\beta}
-	\end{array}\right)\beta + \left(\begin{array}{c}k^u\\ o^{\nu} \\ o^{\hat\zeta}
-	\end{array}\right).
-\end{equation}
-Here $\hat C_2$ is a normalised version of $O^T_\beta(\bar T x + \bar e) = 0$.
-For completeness, the $m=2$ maximisation and its solution are:
-\begin{equation}
-	\hat J_2^\ast(x,u) = \left\{\begin{split}
-	\max_{w,x^+} & -\frac{\gamma^2}{2}\norm{w}^2 + J_{1}^\ast(x^+)\\
-	\text{s.t.} & 
-	\underbrace{\left(\begin{array}{cc}
-	G^\prime & 0 \\ -D & I \\
-	0 & \hat C_2
-	\end{array}\right)}_{\bar A}
-	\left(\begin{array}{c}w\\ x^+\end{array}\right)
-	\\&= \underbrace{\left(\begin{array}{cc}W_x^\prime & W_u^\prime \\ A & B \\ 0 & 0\end{array}\right)}_{
-	\bar S
-	}
-	\left(\begin{array}{c}x \\ u \end{array}\right) + \underbrace{\left(\begin{array}{c}
-	w_c^\prime \\ 0 \\ {\bf{1}}\end{array}\right)}_{\bar b}
-	\end{split}\right.
-\end{equation}
-\begin{equation}
-	\left(\begin{array}{c}
-	w^\ast \\
-	x^{+,\ast} \\
-	\eta^\ast \\
-	\lambda^\ast\\
-	\zeta^\ast
-	\end{array}\right) = \left(\begin{array}{c}M^w_z\\ M^{x^+}_z \\ N^{\eta}_z \\ N^{\lambda}_z \\ N^{\zeta}_z
-	\end{array}\right)z + 
-	\left(\begin{array}{c}0\\ 0 \\ N^{\eta}_{\hat\beta} \\ N^{\lambda}_{\hat\beta} \\ N^\zeta_{\hat\beta}
-	\end{array}\right)\hat\beta + \left(\begin{array}{c}m^w\\ m^{x^+} \\ n^{\eta} \\ n^{\lambda}\\ n^\zeta
-	\end{array}\right)
-\end{equation}
-All subsequent minimisations and maximisations can be solved analogously provided the active set is
-known.
-
-\section{Exact solution of min-max program}\label{sec:line:search}
-In the previous section we presented a recursive algorithm to solve~\eqref{eq:the:problem}
-when all active constraints are known. In this section we present a method to find the active
-constraints for a given initial state $\mathpzc x_e$ using a line search starting from a state $\mathpzc x_0$
-for which the active constraints are known. In section~\ref{sec:gen:mpQP} and~\ref{sec:applied:mpQP}
-we derived an explicit solution for each sub-optimisation program which depended affinely on the
-state~$x$ at that stage~$m$ or the state and the input at that stage. Henceforth we denote the stage 
-with an index, e.g.~$x_m$ denotes the optimised state in stage $m$, that is $x^{+,\ast}$ at stage $m+1$.
-To ensure continuity of the dual variables we choose $\hat\zeta_m = \hat\beta_m$ and $\zeta_m=\beta_{m-1}$.
-The affine character of the solution of each sub-problem allows us to parametrise the entire trajectory
-with respect to parameters at stage~$m=N$, that is $x_N=\mathpzc x_0$ and $\beta_N$.
-
-We recursively define all primal and dual variables:
-\begin{equation}\label{eq:trajectory:affine:representation}
-	\begin{split}
-		u_N(x_N) =& \underbrace{K_{x,N}^x}_{\Psi_N^u} x_N + \underbrace{k_N^u}_{\psi_N^u}\\
-		\nu_N(x_N,\beta_N) &= \underbrace{O_{x,N}^x}_{\Psi_N^\nu} x_N + \underbrace{O_{\beta,N}^\nu}_{\Phi_N^\nu} \beta_N + 
-		\underbrace{o_N^\nu}_{\psi_N^u}\\
-		&\vdots \\
-		x_0(x_N) =& \underbrace{M_{z,1}^{x^+}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right)}_{\Psi_1^x}x_N + 
-		M_{z,1}^{x^+}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + m_1^{x^+}\\
-		\eta_1(x_N,\beta_N) =& \underbrace{\left(N_{z,1}^{\eta}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right) + 
-		N_{\hat\beta,1}^\eta \Psi_1^{\hat\zeta}\right)}_{\Psi_1^\eta}x_N + \underbrace{N_{\hat\beta,1}^\eta \Phi_1^{\hat\zeta}}_{\Phi_1^\eta} \beta_N\\
-		&+\underbrace{N_{z,1}^{\eta}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + 
-		N_{\hat\beta,1}^\eta \psi_1^{\hat\zeta} + n_1^\eta}_{\psi_1^\eta}\\
-		&\vdots
-	\end{split}
-\end{equation}
-Notice that $\Phi^{(\cdot)}_m$ is only non-trivial if the associated sub-problem is degenerate. The 
-representation~\eqref{eq:trajectory:affine:representation} is valid as long as the constraint set remains unchanged, 
-i.e. the inequalities that hold with equality do not change. Starting from the known set of active constraints at
-$\mathpzc x_0$ we perform a line search towards $\mathpzc x_e$, i.e. we vary $x_N(\alpha)=\mathpzc x_0+
-\alpha(\mathpzc x_e-x_0)$ for $0\leq\alpha\leq1$. We use~\eqref{eq:trajectory:affine:representation} to
-check all inactive constraints with the primal variables $x_m(x_N(\alpha)),\, u_m(x_N(\alpha))$ and~$w_m(x_N(\alpha))$,
-and all dual variables corresponding to inequality constraints to check whether constraints need to be deactivated. That is,
-we search for the smallest $\alpha$ such that $\Xi_{m,i}^x x_m(x_N(\alpha))+\Xi_{m,i}^u u_m(x_N(\alpha))=\xi_{m,i}$
-et cetera for the primal variables and the smallest $\eta_{m,i}(x_N(\alpha),\beta_N)=0$ and update the set of active
-constraints accordingly, i.e. if an additional constraint is activated it is introduced to the equality constraint
-mpQP recursion and the updated problems are solved again recursively, if a constraint needs to be deactivated
-because the smallest $\alpha$ corresponds to the zero-crossing of its dual variable then again the mpQP recursion 
-is solved again. The updated active set is the new known active set at $\mathpzc x_0 = x_N(\alpha)$ and the line-search
-continues until the state~$\mathpzc x_e$ is in the same active set as $\mathpzc x_N(\alpha)$ where the line-search terminates.
-To initialise we start at the origin $\mathpzc x_0=0$, since we know that no constraints are active. Notice that the right hand side 
-of~\eqref{eq:dist:cons} is updated the same way, a line-search is used to determine the active affine representation.
-
-If there are compatibility constraints on the initial state, i.e.\ if $\beta_N$ is non-trivial, then $\alpha$ cannot continue 
-to  increase since equality constraints on $x_N(\alpha)$ are active, however $\beta_N$ can be used to update the active set. 
-As in~\cite{Buerger:ACC} the free degeneracy variable $\beta_N$ is chosen to deactivate an active constraint on $x_N(\alpha)$ 
-as long as no inequality constraints would be violated, i.e. as long as no dual variable becomes negative.
-
 \section{Example}\label{sec:example}
@@
 feasible set before reaching the (infeasible) state $\mathpzc x_e=(0,30)$.
-
-\begin{figure}
-\includegraphics[width=.48\textwidth]{res}
-\caption{The light blue sets depict the projected state constraint iterates~$\mathcal X_m$,
-    whereas the blue and pink lines are the state trajectories produced along the two line
-    searches. The pink line search eventually violates the state constraints and terminates.}
-\label{fig:numerical:example}
-\end{figure}
-\section{Conclusion}\label{sec:conclusion}
-
-\bibliographystyle{ifacconf}        % Include this if you use bibtex 
-\bibliography{MyLib}       % and a bib file to produce the 
-								                 % bibliography (preferred). The
-                                 % correct style is generated by
-                                 % Elsevier at the time of printing.
-
-\end{document}

### 2015-04-21 draft_v2.tex
more edits section 5

--- 2015-04-21 draft_v2.tex
@@
 & \!\!\!\!\!\!
-\Lambda_{0,i}(Ax+Bu)+ \!\!\underbrace{\max_{j\in\{1,\dots,r\}}\Lambda_{0,i} Dw_j(x,u)}_{(i)}\leq\lambda_i, \, \forall i\in\mathcal I_0
+\Lambda_{0,i}(Ax+Bu)+ \!\!\underbrace{\max_{j\in\{1,\dots,r\}}\!\Lambda_{0,i} Dw_j(x,u)}_{(i)}\leq\lambda_i, \, \forall i\in\mathcal I_0
 	\Bigr\} \end{aligned}
@@
 \section{Solving min-max quadratic programs as multi-parametric quadratic programs}\label{sec:applied:mpQP}
-In this section we apply the results derived in section~\ref{sec:gen:mpQP} to
-the considered min-max robust control problem~\eqref{eq:the:problem}. We 
-define a recursion and assume the active set is known to obtain a closed solution for~\eqref{eq:the:problem}.
+In this section we apply the results derived in Section~\ref{sec:gen:mpQP} to the considered min-max robust
+control problem~\eqref{eq:the:problem}. For the case that the set of active constraints is known, we define a
+recursion that provides a closed solution for~\eqref{eq:the:problem}.
 %
 %To use an active set solver for the problem:
-First epx
+We first express~\eqref{eq:the:problem} in the form
 \begin{subequations}\label{eq:the:problem:reformulated}%
@@
 \end{subequations}
-with~$J_0^\ast(x^+) = \frac{1}{2}\norm{x^+}_P^2$ and $m=1,\dots,N$. Notice that explicitly using
+with~$J_0^\ast(x^+) = \frac{1}{2}\|x^+\|_{P_0}^2$ and $m=1,\dots,N$. Notice that explicitly using
 $u\in\mathcal U$ is no longer necessary as satisfaction of the input constraints is intrinsic
@@
 We split the sequence of  min-max problems into a sequence of multi-parametric 
-quadratic programs. Starting with the maximisation at stage $m=1$ and using a backward sweep approach (see e.g.~\cite{Bryson:1975}), 
-we obtain
-\begin{equation}
+quadratic programs. Starting with the maximisation at stage $m=1$ and using a backward sweep approach
+\citep[see e.g.][]{Bryson:1975}, 
+this yields
+\[
 	\hat J_m^\ast(x,u) = \left\{\begin{split}
-    \max_{w,x^+} & -\frac{\gamma^2}{2}\norm{w}^2 + J_{m-1}^\ast(x^+)\\
-    \text{s.t.} & \begin{array}{rcl}
+    \max_{w,x^+}\ & {-\frac{\gamma^2}{2}}\norm{w}^2 + J_{m-1}^\ast(x^+)\\
+    \text{s.t. }\  & \begin{array}[t]{rcl}
     Gw & \leq & H(x,u)\\
@@
     \end{split}\right.
-\end{equation}
+\]
 and
-\begin{equation}
+\[
 	J_m^\ast(x) = \left\{\begin{split}
-    \min_{u} & \frac{1}{2}\left(\norm{x}^2_Q + \norm{u}_R^2\right) + \hat J_m^\ast(x,u)\\
-    \text{s.t.} & \begin{array}{ccccl}
+    \min_{u}\ & \frac{1}{2}\left(\norm{x}^2_Q + \norm{u}_R^2\right) + \hat J_m^\ast(x,u)\\
+    \text{s.t.}\ & \begin{array}[t]{ccccl}
     \Xi^x_m x &+& \Xi^u_m u &\leq &\xi_m\\
@@
     \right.
-\end{equation}
+\]
 Suppose the active set is given, i.e.~it is known which inequality constraints hold with equality. 
 For notational convenience we denote active inequalities with $(\cdot)^\prime$, e.g.  $(\Xi^x_m)^\prime x + (\Xi^u_m)^\prime u = \xi_m^\prime$. 
-Since $J^\ast_0(x^+) = \frac{1}{2}\norm{x^+}_{P_0}^2$ is a given function, compatibility constraints are not necessary at 
+Given that $J^\ast_0(x^+) = \frac{1}{2}\|x^+\|_{P_0}^2$, compatibility constraints are not necessary at 
 stage $m=1$ and the maximisation problem is given by:
-\begin{equation}
+\[
 	\hat J_1^\ast(x,u) = \left\{\begin{split}
-	\max_{w,x^+} & -\frac{\gamma^2}{2}\norm{w}^2 + J_{0}^\ast(x^+)\\
-	\text{s.t.} & 
+	\max_{w,x^+} \ & {-\frac{\gamma^2}{2}}\norm{w}^2 + J_{0}^\ast(x^+)\\
+	\text{s.t. }\ & 
 	\underbrace{\left(\begin{array}{cc}
@@
 	\end{split}\right.
-\end{equation}
+\]
 with $W_x^\prime, W_u^\prime$ and $w_c^\prime$ denoting the active rows of the right hand side 
@@
 With Lemma~\ref{lem:mpQP:solution} we obtain
-\begin{equation}
+\[
       \left(\begin{array}{c}
@@
       \end{array}\right)
-\end{equation}
+\]
 where $\eta^\ast$ denotes the dual variable to the active inequality constraints and hence must
-be non-negative, i.e.~$\eta^\ast\geq0$. Notice that we omitted stage indices to avoid overloaded notation.
+be non-negative, i.e.~$\eta^\ast\geq0$. Notice that we omit stage indices to avoid overloaded notation.
 The cost-to-go for the minimisation problem at stage $m=1$ is
@@
 constraints for a given initial state $\mathpzc x_e$ using a line search starting from a state $\mathpzc x_0$
-for which the active constraints are known. In section~\ref{sec:gen:mpQP} and~\ref{sec:applied:mpQP}
+for which the active constraints are known. In Section~\ref{sec:gen:mpQP} and~\ref{sec:applied:mpQP}
 we derived an explicit solution for each sub-optimisation program which depended affinely on the

### 2015-04-21 draft_v2.tex
section 6 and abstract

@@
 
-\title{Robust receding horizon control for linear systems with state dependent disturbance}
+\title{Robust receding horizon control for linear systems with state and input dependent disturbances}
 
@@
 \begin{abstract}                % Abstract of not more than 250 words.
-
+  A robust model predictive controller is proposed for constrained linear systems with unknown disturbances
+  that are subject to state and input dependent piecewise affine bounds.
+  % with a dependence on the system state and control input. 
+  The formulation encompasses problems involving model uncertainty arising from unknown system
+  parameters and linearisation errors. We propose a computationally efficient method for the online
+  optimization of a receding horizon min-max cost over the class of feedback strategies subject robust
+  constraint satisfaction and provide illustrative numerical examples.
 \end{abstract}
@@
 \begin{keyword}
--
+Robust optimal control, min-max control, multiparametric programming 
 \end{keyword}
@@
 To make it possible to obtain a closed form solution of the min-max optimal control problem we assume a
-linear-quadratic problem formulation. Thus we assume the linear dynamic model 
+linear-quadratic problem formulation. Thus we assume linear dynamics 
 \begin{equation}\label{eq:system:equation}
@@
 We define $\mathcal{X}^\infty$ as the maximal robust positive invariant (MRPI) set \citep{blanchini:2007}), for the closed-loop system governed by a fixed state feedback controller
-$u=Kx$, so that 
+$u=Kx$:
 %
@@
 where $\eta^\ast$ denotes the dual variable to the active inequality constraints and hence must
-be non-negative, i.e.~$\eta^\ast\geq0$. Notice that we omit stage indices to avoid overloaded notation.
+be non-negative, i.e.~$\eta^\ast\geq0$. Notice that to avoid
+overloaded notation we have omitted the stage indices.
 The cost-to-go for the minimisation problem at stage $m=1$ is
-\begin{equation}
+\[
 	\hat J_1^\ast(z) = \frac{1}{2}z^T
     \hat Q_1 z + c_1 z + d_1
-\end{equation}
+\]
 and the compatibility constraint is given by
@@
 \end{equation}
-i.e.\ $C_1^x$ and $C_1^u$ are given as a row wise normalised version of~\eqref{prototype:compatibility:conditions}.
+i.e.\ $C_1^x$ and $C_1^u$ enforce a row wise normalised version of~\eqref{prototype:compatibility:conditions}.
 Hence the minimisation problem at $m=1$ becomes
-\begin{equation}
+\[
 	J_1^\ast(x) = \left\{\begin{split}
-	\min_{u} & \frac{1}{2}\left(\norm{x}^2_Q + \norm{u}_R^2\right) + \hat J_{1}^\ast(x,u)\\
-    \text{s.t.} & 
+	\min_{u} \ & \frac{1}{2}\left(\norm{x}^2_Q + \norm{u}_R^2\right) + \hat J_{1}^\ast(x,u)\\
+    \text{s.t.} \ & 
     \underbrace{\left(\begin{array}{c}
@@
     \end{split}\right.
-\end{equation}
+\]
 and its solution is given by
-\begin{equation}
+\[
 	\left(\begin{array}{c}
@@
 	\hat\zeta^\ast
-	\end{array}\right) = \left(\begin{array}{c}K^u_x\\ O^{\nu}_x \\ O^{\hat\zeta}_x
+	\end{array}\right) = \left(\begin{array}{c}K^u_x\\ L^{\nu}_x \\ L^{\hat\zeta}_x
 	\end{array}\right)x + 
-	\left(\begin{array}{c}0\\ O^{\nu}_\beta \\ O^{\hat\zeta}_{\beta}
-	\end{array}\right)\beta + \left(\begin{array}{c}k^u\\ o^{\nu} \\ o^{\hat\zeta}
+	\left(\begin{array}{c}0\\ L^{\nu}_\beta \\ L^{\hat\zeta}_{\beta}
+	\end{array}\right)\beta + \left(\begin{array}{c}k^u\\ l^{\nu} \\ l^{\hat\zeta}
 	\end{array}\right).
-\end{equation}
-Here $\hat C_2$ is a normalised version of $O^T_\beta(\bar T x + \bar e) = 0$.
-For completeness, the $m=2$ maximisation and its solution are:
-\begin{equation}
+\]
+For completeness the $m=2$ maximisation and its solution are given as
+\begin{gather*}
 	\hat J_2^\ast(x,u) = \left\{\begin{split}
-	\max_{w,x^+} & -\frac{\gamma^2}{2}\norm{w}^2 + J_{1}^\ast(x^+)\\
-	\text{s.t.} & 
+	\max_{w,x^+} \ & {-\frac{\gamma^2}{2}}\norm{w}^2 + J_{1}^\ast(x^+)\\
+	\text{s.t. }\ & 
 	\underbrace{\left(\begin{array}{cc}
@@
 	\end{split}\right.
-\end{equation}
-\begin{equation}
+\\
 	\left(\begin{array}{c}
@@
 	\end{array}\right)
-\end{equation}
+\end{gather*}
+where $\hat C_2 x = {\bf{1}}$ is a normalised version of $L^T_\beta(\bar T x + \bar e) = 0$.
 All subsequent minimisations and maximisations can be solved analogously provided the active set is
@@
 \section{Exact solution of min-max program}\label{sec:line:search}
-In the previous section we presented a recursive algorithm to solve~\eqref{eq:the:problem}
+The previous section presents a recursive algorithm to solve~\eqref{eq:the:problem}
 when all active constraints are known. In this section we present a method to find the active
-constraints for a given initial state $\mathpzc x_e$ using a line search starting from a state $\mathpzc x_0$
-for which the active constraints are known. In Section~\ref{sec:gen:mpQP} and~\ref{sec:applied:mpQP}
-we derived an explicit solution for each sub-optimisation program which depended affinely on the
+constraints for a given initial state $\chi_e$ using a line search starting from a state $\chi_0$
+for which the active constraints are known. In Sections~\ref{sec:gen:mpQP} and~\ref{sec:applied:mpQP}
+we derived an explicit solution for each optimisation sub-problem which depends affinely on the
 state~$x$ at that stage~$m$ or the state and the input at that stage. Henceforth we denote the stage 
@@
 The affine character of the solution of each sub-problem allows us to parametrise the entire trajectory
-with respect to parameters at stage~$m=N$, that is $x_N=\chi_0$ $x_N=\mathpzc x_0$ and $\beta_N$.
+with respect to parameters at stage~$m=N$, that is $x_N=\chi_0$ and $\beta_N$.
 
@@
 		u_N(x_N) =& \underbrace{K_{x,N}^x}_{\Psi_N^u} x_N + \underbrace{k_N^u}_{\psi_N^u}\\
-		\nu_N(x_N,\beta_N) &= \underbrace{O_{x,N}^x}_{\Psi_N^\nu} x_N + \underbrace{O_{\beta,N}^\nu}_{\Phi_N^\nu} \beta_N + 
-		\underbrace{o_N^\nu}_{\psi_N^u}\\
+		\nu_N(x_N,\beta_N) &= \underbrace{L_{x,N}^x}_{\Psi_N^\nu} x_N + \underbrace{L_{\beta,N}^\nu}_{\Phi_N^\nu} \beta_N + 
+		\underbrace{l_N^\nu}_{\psi_N^u}\\
 		&\vdots \\
 		x_0(x_N) =& \underbrace{M_{z,1}^{x^+}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right)}_{\Psi_1^x}x_N + 
-		M_{z,1}^{x^+}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + m_1^{x^+}\\
+		\underbrace{M_{z,1}^{x^+}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + m_1^{x^+}}_{\psi^x_1}\\
 		\eta_1(x_N,\beta_N) =& \underbrace{\left(N_{z,1}^{\eta}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right) + 
@@
 Notice that $\Phi^{(\cdot)}_m$ is only non-trivial if the associated sub-problem is degenerate. The
-representation~\eqref{eq:trajectory:affine:representation} is valid as long as the constraint set remains unchanged, 
-i.e. the inequalities that hold with equality do not change. Starting from the known set of active constraints at
-$\mathpzc x_0$ we perform a line search towards $\mathpzc x_e$, i.e. we vary $x_N(\alpha)=\mathpzc x_0+
-\alpha(\mathpzc x_e-x_0)$ for $0\leq\alpha\leq1$. We use~\eqref{eq:trajectory:affine:representation} to
-check all inactive constraints with the primal variables $x_m(x_N(\alpha)),\, u_m(x_N(\alpha))$ and~$w_m(x_N(\alpha))$,
-and all dual variables corresponding to inequality constraints to check whether constraints need to be deactivated. That is,
-we search for the smallest $\alpha$ such that $\Xi_{m,i}^x x_m(x_N(\alpha))+\Xi_{m,i}^u u_m(x_N(\alpha))=\xi_{m,i}$
-et cetera for the primal variables and the smallest $\eta_{m,i}(x_N(\alpha),\beta_N)=0$ and update the set of active
-constraints accordingly, i.e. if an additional constraint is activated it is introduced to the equality constraint
-mpQP recursion and the updated problems are solved again recursively, if a constraint needs to be deactivated
-because the smallest $\alpha$ corresponds to the zero-crossing of its dual variable then again the mpQP recursion 
-is solved again. The updated active set is the new known active set at $\mathpzc x_0 = x_N(\alpha)$ and the line-search
-continues until the state~$\mathpzc x_e$ is in the same active set as $\mathpzc x_N(\alpha)$ where the line-search terminates.
-To initialise we start at the origin $\mathpzc x_0=0$, since we know that no constraints are active.
+representation~\eqref{eq:trajectory:affine:representation} is valid as long as the constraint set remains
+unchanged, i.e.\ the inequalities that hold with equality do not change. Starting from the known set of active
+constraints at $\chi_0$ we perform a line search towards $\chi_e$, i.e. we vary
+$x_N(\alpha)=\chi_0+ \alpha(\chi_e-x_0)$ for $0\leq\alpha\leq1$. We
+use~\eqref{eq:trajectory:affine:representation} to check all inactive constraints with the primal variables
+$x_m(x_N(\alpha)),\, u_m(x_N(\alpha))$ and~$w_m(x_N(\alpha))$, and all dual variables corresponding to
+inequality constraints to check whether constraints need to be deactivated. That is, we search for the
+smallest $\alpha$ such that $\Xi_{m,i}^x x_m(x_N(\alpha))+\Xi_{m,i}^u u_m(x_N(\alpha))=\xi_{m,i}$ or
+$G_iw_m(x_N(\alpha))=1$ or $\eta_{m,i}(x_N(\alpha),\beta_N)=0$ for some $m$ and $i$, and update the set of active
+constraints accordingly, i.e. if an additional constraint is activated it is introduced to the equality
+constraint mpQP recursion and the updated problems are solved again recursively, if a constraint is
+deactivated because the smallest $\alpha$ corresponds to the zero-crossing of its dual variable then it is
+removed and the
+mpQP recursion is solved again. The updated active set is the new known active set at $\chi_0 = x_N(\alpha)$
+and the line-search continues until the state~$\chi_e$ is in the same active set as $\chi_N(\alpha)$ where the
+line-search terminates.  To initialise we start at the origin $\chi_0=0$, since we know that no constraints
+are active.
 
-Notice that in since the right hand side of~\eqref{eq:PWA:def:disturbance} is considered to be piecewise affine, the active 
+Notice that since the right hand side of~\eqref{eq:PWA:def:disturbance} is considered to be piecewise affine, the active 
 affine function needs to be determined in a similar fashion. Elementwise $H(x_k(\alpha),u_k(\alpha))$ reduces to 
-\begin{equation}
-\Resize{
+\[
 \begin{split}
-	H_i(x_k(\alpha),u_k(\alpha)) &= \max_j\{\left(H^x_{i,j} \Psi^x_k +H^u_{i,j}\Psi^u_k\right)x_N(\alpha) + 
-	\left(H^x_{i,j} \psi^x_k +H^u_{i,j}\psi^u_k + h_{i,j}\right) \}\\
+	H_i(x_k(\alpha),u_k(\alpha)) &= \begin{aligned}[t] \max_j\{ & \left(H^x_{i,j} \Psi^x_k
+          +H^u_{i,j}\Psi^u_k\right)x_N(\alpha)\\
+        & + \left(H^x_{i,j} \psi^x_k +H^u_{i,j}\psi^u_k + h_{i,j}\right) \}
+        \end{aligned}\\
 	&=\max_j f_j\alpha + g_j
 	\end{split}
-}
-\end{equation}
+\]
 which we can rewrite as
@@
 \end{equation}
-So elementwise the determination of the active affine representation is a multi-parametric linear program, see e.g.~\cite{Gal:1995},
-that has to be solved in every active set update. So that $W_x^\prime,\,W_u^\prime$ and $w^\prime_c$ remain the active
-solution. This can be done by computing the vertices of $\mathcal H = \{(t,\alpha):0\leq\alpha\leq1\wedge
-f_j\alpha+g_j\leq t\;\forall j\}$ and ordering the vertices such that $0=\alpha_1\leq\alpha_2\leq\dots$ the solution
-that has to be considered in the line search is given by $\alpha_2$.
+Thus the elementwise determination of the active affine representation is a multi-parametric linear program
+\citep[see e.g.][]{Gal:1995} that has to be solved in every active set update in order that $W_x^\prime,\,W_u^\prime$
+and $w^\prime_c$ provide the active solution. This can be done by computing the vertices of
+$\mathcal H = \{(t,\alpha):0\leq\alpha\leq1\wedge f_j\alpha+g_j\leq t\;\forall j\}$ and ordering the vertices
+such that $0=\alpha_1\leq\alpha_2\leq\dots$ the solution that has to be considered in the line search is then given
+by $\alpha_2$.
 

### 2015-04-21 example.tex
Preliminary synch.

@@
+%!TEX root = draft_v2.tex
 \section{Example}\label{sec:example}
-This section we present a numerical simulation in which the state-dependent uncertainty enters through an upper bound on the linearisation
-error for a nonlinear system. We consider an inverted pendulum described by $ml^2\ddot\varphi = mlg\sin\varphi+M$, where
-$m=0.1$\,kg is the mass, $l=0.3$\,m is the length of the pendulum, $g=9.81$\,m\,s$\mbox{}^{-2}$ is the gravitational
-constant and $M$ is the direct torque input. Discretisation using Euler backward finite differences 
-at $f = 20$\,Hz yields
-\begin{equation}
-  \begin{split}
-    x_1[k+1] &= x_1[k] + \frac{1}{f} x_2[k]\\
-    x_2[k+1] &= \frac{g}{fl} \sin(x_1[k]) + x_2[k] + \frac{1}{fml^2}u[k]
-  \end{split}
-\end{equation}
-where $x_1[k] = \varphi(t_0+k/f),x_2[k] = \dot\varphi(t_0+k/f)$ and $u[k] = M(t_0+k/f)$.
-The nonlinearity is given by the sine function, and we can explicitly state the 
-linearisation error as $e(x_1)=\frac{g}{fl}(\sin x_1 - x_1)$. Since the linearisation
-only approximates the nonlinear dynamics around the equilibrium we can choose a closed interval 
-$0\in D\subset\mathbb R$ and maximise the upper bound 
-\begin{equation}
-  \Delta e = \max_{x_1\in D}\abs{\frac{de}{dx_1}} = \frac{g}{fl}\max_{x_1\in D}\abs{\cos x_1-1}.
-\end{equation}
-This results in the linear system
-\begin{equation}
-  x^+ = \underbrace{\left(\begin{array}{cc}
-  1 & f^{-1}\\ g(fl)^{-1} & 1
-  \end{array}\right)}_A x + \underbrace{\left(\begin{array}{c} 0 \\(ml^2f)^{-1} \end{array}\right)}_B u
-  +\left(\begin{array}{c}w_1\\ w_2\end{array}\right)
-\end{equation}
-with $\abs{w_1}\leq w_{1,\max}$ and $\abs{w_2}\leq\max\{w_{2,\max},\Delta e \abs{x_1}\}$.
-We also introduce the input constraint $\abs{u}\leq3$\,N\,m and use the interval $D = [-\frac{3\pi}{4},
-\frac{3\pi}{4}]$ and a horizon of $N=7$ to obtain the sequence of state constraints $\mathcal X_m$
-depicted in Figure~\ref{fig:numerical:example}. The line search starting at the origin and
-exploring towards $\mathpzc x_e=(-6,50)$ produces the optimal trajectories at the active-set switches
-which are illustrated in blue. In pink a warm-started line search terminates on the boundary of the
-feasible set before reaching the (infeasible) state $\mathpzc x_e=(0,30)$.
+In this section we present a numerical simulation for a simplified levitating ball model, as derived in 
+by~\cite{Schaich:2015}. The dynamics of the nonlinear system are given $m\ddot y = m g - c\frac{i^2}{y^2}$,
+where $m$ denotes the mass of the ball, $g$ denotes the gravitation constant, $c$ denotes a constant depending
+on the coil, $y$ the vertical distance to the coil, the simplification is due to neglecting inductive dynamics 
+and assuming we that can influence the current~$i$ directly. Figure~\ref{fig:levitating:ball} illustrates the setup.
+Choosing the state $x=(y,\dot y)$ and the input $u=i$ we obtain a state space representation which depends nonlinearly
+on both the state and the input. An equilibrium is given for all $u=\sqrt{\frac{gm}{c}}x_1$.
+
+Linearising the nonlinear differential 
+equation $\dot x = f(x,u)$ around an equilibrium point $(\hat x, \hat
+u)$ gives the approximate linear model 
+%
+\[
+	 \Delta\dot{x} = \underbrace{\left(\begin{array}{cc}
+	0 & 1 \\ \frac{2c\hat u^2}{m\hat x_1^3} & 0
+	\end{array}\right)}_{\frac{\partial f}{\partial x}(\hat x,\hat
+      u)}\Delta x 
++ \underbrace{\left(\begin{array}{c}
+	0 \\ - \frac{2c\hat u}{m\hat x_1^2}
+	\end{array}\right)}_{\frac{\partial f}{\partial u}(\hat x,\hat
+      u)}\Delta u
+\]
+%
+where $\Delta u = u -\hat{u}$ and $\Delta x \approx x-\hat{x}$.
+We derive the discrete time dynamics with sampling rate $T_s$ using
+the Euler formula $x^+=x+T_s f(x,u) =:\tilde f(x,u)$ giving
+\[
+\Delta x^+ = A \Delta x + B \Delta u , \quad
+\Biggl\{\begin{aligned} A &= I+T_s\frac{\partial f}{\partial  x}(\hat
+  x,\hat u) \\
+B &= T_s \frac{\partial f}{\partial u}(\hat x,\hat u)
+\end{aligned}
+\]
+%
+A representation of the form~\eqref{eq:the:problem}
+
+\begin{figure}
+\centering
+% \begin{overpic}[scale=0.75]{levitatingBall}
+% \put(30,5){$m g$}
+% \put(30,41){$c\frac{i^2}{x^2}$}
+% \put(78,28){$y$}
+% \put(90,89){$i$}
+% \end{overpic}
+\begin{lpic}{levitatingBall(.75,)}
+\lbl[tr]{25,3; $m g$}
+\lbl[br]{25,25; $c\frac{i^2}{y^2}$}
+\lbl[bl]{49,17; $y$}
+\lbl[bl]{56,55; $i$}
+\end{lpic}
+\vspace{-2mm}
+\caption{Levitating ball system.}
+\label{fig:levitating:ball}
+\end{figure}
+
+% This section we present a numerical simulation in which the state-dependent uncertainty enters through an upper bound on the linearisation
+% error for a nonlinear system. We consider an inverted pendulum described by $ml^2\ddot\varphi = mlg\sin\varphi+M$, where
+% $m=0.1$\,kg is the mass, $l=0.3$\,m is the length of the pendulum, $g=9.81$\,m\,s$\mbox{}^{-2}$ is the gravitational
+% constant and $M$ is the direct torque input. Discretisation using Euler backward finite differences 
+% at $f = 20$\,Hz yields
+% \begin{equation}
+%   \begin{split}
+%     x_1[k+1] &= x_1[k] + \frac{1}{f} x_2[k]\\
+%     x_2[k+1] &= \frac{g}{fl} \sin(x_1[k]) + x_2[k] + \frac{1}{fml^2}u[k]
+%   \end{split}
+% \end{equation}
+% where $x_1[k] = \varphi(t_0+k/f),x_2[k] = \dot\varphi(t_0+k/f)$ and $u[k] = M(t_0+k/f)$.
+% The nonlinearity is given by the sine function, and we can explicitly state the 
+% linearisation error as $e(x_1)=\frac{g}{fl}(\sin x_1 - x_1)$. Since the linearisation
+% only approximates the nonlinear dynamics around the equilibrium we can choose a closed interval 
+% $0\in D\subset\mathbb R$ and maximise the upper bound 
+% \begin{equation}
+%   \Delta e = \max_{x_1\in D}\abs{\frac{de}{dx_1}} = \frac{g}{fl}\max_{x_1\in D}\abs{\cos x_1-1}.
+% \end{equation}
+% This results in the linear system
+% \begin{equation}
+%   x^+ = \underbrace{\left(\begin{array}{cc}
+%   1 & f^{-1}\\ g(fl)^{-1} & 1
+%   \end{array}\right)}_A x + \underbrace{\left(\begin{array}{c} 0 \\(ml^2f)^{-1} \end{array}\right)}_B u
+%   +\left(\begin{array}{c}w_1\\ w_2\end{array}\right)
+% \end{equation}
+% with $\abs{w_1}\leq w_{1,\max}$ and $\abs{w_2}\leq\max\{w_{2,\max},\Delta e \abs{x_1}\}$.
+% We also introduce the input constraint $\abs{u}\leq3$\,N\,m and use the interval $D = [-\frac{3\pi}{4},
+% \frac{3\pi}{4}]$ and a horizon of $N=7$ to obtain the sequence of state constraints $\mathcal X_m$
+% depicted in Figure~\ref{fig:numerical:example}. The line search starting at the origin and
+% exploring towards $\mathpzc x_e=(-6,50)$ produces the optimal trajectories at the active-set switches
+% which are illustrated in blue. In pink a warm-started line search terminates on the boundary of the
+% feasible set before reaching the (infeasible) state $\mathpzc x_e=(0,30)$.

### 2015-04-21 example.tex
Changes made to example sec, and complexity sec.

@@
 %!TEX root = draft_v2.tex
+\section{Complexity}\label{sec:complexity}
+The computational complexity of the considered algorithm can easily be bounded. In order to give implementation
+free bounds we specify only floating point operations (flops). For each given active set the solver has
+to solve at most $2N$ mpQPs, which is done by decomposing the problem as stated in section~\ref{sec:gen:mpQP},
+in the worst case this requires one QR decomposition, with $\frac{4}{3}n^3$ flops, and one Cholesky decomposition,
+with $\frac{n^3}{3}$ flops, where $n$ is the number of optimisation variables. Solving the worst case problem
+on one stage therefore requires $\frac{5}{3}(2n_x^3+n_u^3)$ flops, in the worst case $N$ stages need to be solved,
+so that the worst case computational burden for the solution of the mpQP sequence is given 
+by~$\frac{5N}{3}(2n_x^3+n_u^3)$. To the authors' best knowledge there are no sensible bounds on the number of
+active set changes, so that no bound can be given on the number of times the sequence has to be solved.
+In section~\ref{sec:example} we state the case of an example system with an implementation in MATLAB.
+
 \section{Example}\label{sec:example}
@@
 %
-A representation of the form~\eqref{eq:the:problem}
+A representation of the form~\eqref{eq:the:problem} can be obtained by sampling input and state
+constraints and using the mean-value theorem, as elaborated by~\cite{Schaich:2015}. This leads
+to a disturbance representation of the form $\mathcal W(x,u)=\{w\in\mathbb R^n: 
+\min_{k\in\mathcal S_w}\{ H_{k,i}^x x + H_{k,i}^u u\} \leq w_i \leq \max_{k\in\mathcal S_w} 
+\{ H_{k,i}^x x + H_{k,i}^u u \} \}$,
+where ${k\in\mathcal S_w}$ denotes the sample index and $i$ the row number. This point-wise polytopic representation
+in addition with a polyhedral representation of state constraints allows us to compute a polyhedral
+MRPI set~$\mathcal X^\infty$. As a terminal feedback controller $K$ we use the solution to the robust 
+Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2 w^Tw$ 
+with $V(x)=x^T P_0 x\geq0$, i.e. $x^TP_0x - ((A+BK)x+Dw)^TP_0((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^T w$, 
+see e.g.~\cite{Boyd:94}. This semi-definite program also returns a value for $\gamma^2$. Starting from 
+a polyhedral MRPI set~$\mathcal X^\infty$ we apply the algorithm presented in section~\ref{sec:preliminaries}
+to obtain the necessary stage constraints~$\mathcal Z_k$. At this stage we can introduce numerical values
+for individual parameters, we use $T_s=30ms, C=1\frac{kg m^3}{A^2s^2}, m=100g, \hat x_1 = 50mm$ and $\mathcal X=\{x:
+\abs{x_1- \hat x_1}\leq 1mm\wedge \abs{x_2}\leq 105\frac{mm}{s}\}$, $\mathcal U=\{u:\abs{ u-\hat u}\leq10mA\}$.
+To obtain $\mathcal W(x,u)$ we sample $\mathcal X$ and $\mathcal U$ with a total of 25 samples, i.e. the cardinality
+of $\mathcal S_w$ is 10. In the simulation we use horizon length $N=5$. We perform a cold started line search from $\chi_0=(0,0)$
+to the outer bound of the constraint set at $\chi_e=(1,-30)$, the resulting trajectories at the boundaries of
+individual active sets are plotted in figure~\ref{fig:plot}.
+
+The simulation was implemented in MATLAB only using non optimised in-built functions for the main computational
+purposes. In the simulation illustrated in figure~\ref{fig:plot} there were a total of 10 iterations required,
+out of which 7 correspond to changes of the dominating right hand side of $\mathcal W(x,u)$, for which no recomputation
+of the solution is necessary. Performing the entire linesearch to the boundary of the feasible set took $0.3765s$.
 
@@
 \label{fig:levitating:ball}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{myplot}
+\caption{Projected stage constraints $\mathcal X_i, i=1,\dots,N$ in red. Trajectories
+at the active set changes and on the boundary in blue.}
+\label{fig:plot}
 \end{figure}

### 2015-04-22 example.tex
Corrected typo.
Included explicit flop count.

@@
 free bounds we specify only floating point operations (flops). For each given active set the solver has
-to solve at most $2N$ mpQPs, which is done by decomposing the problem as stated in section~\ref{sec:gen:mpQP},
-in the worst case this requires one QR decomposition, with $\frac{4}{3}n^3$ flops, and one Cholesky decomposition,
-with $\frac{n^3}{3}$ flops, where $n$ is the number of optimisation variables. Solving the worst case problem
-on one stage therefore requires $\frac{5}{3}(2n_x^3+n_u^3)$ flops, in the worst case $N$ stages need to be solved,
-so that the worst case computational burden for the solution of the mpQP sequence is given 
-by~$\frac{5N}{3}(2n_x^3+n_u^3)$. To the authors' best knowledge there are no sensible bounds on the number of
+to solve at most $2N$ mpQPs, which is done by decomposing the problem as stated in section~\ref{sec:gen:mpQP}.
+For each mpQP the main computational effort is used the computation of $\Sigma$ in~\eqref{seq:sigma}.
+In the case~\eqref{eq:sigma:normal}, this requires a QR decomposition with $2(mn^2-n^3/3)$ flops 
+($m$ the number of active constraints and $n$ the number of optimisation variables), the inversion of a 
+triangular matrix with $(m^3-m)/6$ flops and several matrix multiplications with $mpn$ flops (for the multiplication
+of a $m\times n$ matrix with a $n\times p$ matrix).
+The computationally more expensive case~\eqref{eq:sigma:degen}, requires a QR decomposition, the inversion of a
+definite matrix $W$, which can be done using the Cholesky decomposition with $n^3/3$ flops and the inversion of a 
+triangular matrix, it again requires several matrix multiplications and additions with $mn$ flops and one additional 
+inversion of a definite matrix $\Delta$. In the worst case this adds up to $11n^3+n^2-n/3$ flops to obtain $\Sigma$
+in the worst case scenario. The solution to the problem is then the result of a matrix multiplication, in order to 
+be able to solve the subsequent mpQP the matrix $W_\theta$ and the vector $c_\theta$ have to be computed so that the over
+all flop count in the worst case adds up to $11n^3+n^2+2/3n+2n^2 n_\theta$, where $n_\theta$ denotes the dimension of the
+parameter~$\theta$. At each stage two mpQPs have to be solved recursively, so that in the worst case the recursion
+for the entire horizon requires $N(2 n_x+5 n_x^2+101 n_x^3+8 n_x^2 (n_u+n_x))$ flops.
+
+To the authors' best knowledge there are no sensible bounds on the number of
 active set changes, so that no bound can be given on the number of times the sequence has to be solved.
@@
 
-The simulation was implemented in MATLAB only using non optimised in-built functions for the main computational
+The simulation was implemented in MATLAB only using non optimised built-in functions for the main computational
 purposes. In the simulation illustrated in figure~\ref{fig:plot} there were a total of 10 iterations required,

### 2015-04-22 draft_v2.tex
Preliminary synch.
Made some changes to separate the example cleanly.
Included explicit flop count.
sections 7-9

@@
 \usepackage{mathrsfs}
+\usepackage{lpic}
 
@@
   optimization of a receding horizon min-max cost over the class of feedback strategies subject robust
-  constraint satisfaction and provide illustrative numerical examples.
+  constraint satisfaction and provide an illustrative numerical example.
 \end{abstract}
@@
 After describing the control problem in Section~\ref{sec:problem:statement} we summarise preliminary 
-results which are necessary to formulate the considered problem explicitly (Section~\ref{sec:preliminaries}).
+results which are necessary to formulate the considered problem explicitly in Section~\ref{sec:preliminaries}.
 Section~\ref{sec:gen:mpQP} discusses the recursive solution for equality constrained min-max recursions, one of 
 the essential parts of the active set solver, and this is applied to the min-max RMPC problem in Section~\ref{sec:applied:mpQP}
-for the case that the active set of constraints is known. A line search to determine the active set of constraints is presented
-in Section~\ref{sec:line:search}. The application of the proposed algorithm to an example problem is presented in 
+for the case that the active set of constraints is known. A line search to determine the active set of
+constraints is described 
+in Section~\ref{sec:line:search} and bounds on the computational complexity of the approach are discussed in
+Section~7. An application of the proposed algorithm to an example problem is presented in 
 Section~\ref{sec:example} and conclusions are drawn in Section~\ref{sec:conclusion}.
@@
 \Sigma (0,S^T)^T$ and $N_\beta=Q_2$, where 
-\[
+\begin{subequations}\label{seq:sigma}
+\begin{equation}\label{eq:sigma:normal}
 	\Sigma = \left(\begin{array}{cc}
@@
 	\end{array}\right) .
-\]
+\end{equation}
 On the other hand if rank$(H)<\min\{n_y,n_\lambda\}$ (so that $H$ is rank deficient), then
-\[
+\begin{equation}\label{eq:sigma:degen}
 	\Sigma = \left(\begin{array}{cc}
@@
 	\end{array}\right)
-\]
+\end{equation}
+\end{subequations}
 with $\Delta = (RW^{-1}R^T)^{-1}$. This concludes the proof.
@@
 
-\begin{figure}
-\includegraphics[width=.48\textwidth]{res}
-\caption{The light blue sets depict the projected state constraint iterates~$\mathcal X_m$,
-    whereas the blue and pink lines are the state trajectories produced along the two line
-    searches. The pink line search eventually violates the state constraints and terminates.}
-\label{fig:numerical:example}
-\end{figure}
 \section{Conclusion}\label{sec:conclusion}
+We have proposed a receding horizon controller for linearly constrained linear systems with unknown
+disturbances that are subject to state and input dependent bounds. The optimisation of predicted feedback laws
+is performed using an efficient specialised active set solver. Future work will consider how to limit the number of active set changes while retaining
+the guarantee of closed loop stability.
 

### 2015-04-22 example.tex
sections 7-9

--- 2015-04-21 example.tex
@@
 %!TEX root = draft_v2.tex
+\section{Complexity}\label{sec:complexity}
+We next discuss bounds on the computational complexity of the algorithm outlined in Section~\ref{sec:line:search}.
+%The computational complexity of the considered algorithm can easily be bounded. 
+%In order to give implementation-free bounds  these are expressed 
+%These are given in terms of floating point operations
+%(flops). 
+For a given active set at most $2N$ mpQPs must be solved, and this is done by decomposing the
+problem as stated in section~\ref{sec:gen:mpQP}.  For each mpQP the main computational effort is to
+determine $\Sigma$ in~\eqref{seq:sigma}. In the case of~\eqref{eq:sigma:normal} this requires a QR
+decomposition with $2(mn^2-n^3/3)$ floating point operations (flops), where $m$ is the number of active constraints and $n$ the number of
+optimisation variables, plus inversion of a triangular matrix with $(m^3-m)/6$ flops and several matrix
+multiplications with $mpn$ flops (for the multiplication of a $m\times n$ matrix with a $n\times p$
+matrix). The computationally more expensive case of~\eqref{eq:sigma:degen} requires a QR decomposition,
+inversion of a definite matrix $W$ using Cholesky decomposition with $n^3/3$ flops, inversion of a triangular
+matrix, several matrix multiplications and additions with $mn$ flops, and inversion of a definite matrix
+$\Delta$. In the worst case this adds up to at most $11n^3+n^2-n/3$ flops to obtain $\Sigma$. The solution to
+the problem is then the result of a matrix multiplication, and, in order to be able to solve the subsequent
+mpQP, the matrix $W_\theta$ and the vector $c_\theta$ also need to be computed. Hence the overall flop count
+in the worst case adds up to $11n^3+n^2+2/3n+2n^2 n_\theta$, where $n_\theta$ denotes the dimension of the
+parameter~$\theta$. 
+%At each stage two mpQPs have to be solved recursively, so that 
+In the worst case the
+recursion for the entire horizon therefore requires $N(2 n_x+5 n_x^2+101 n_x^3+8 n_x^2 (n_u+n_x))$ flops.
+
+The number of active set changes needed to obtain the active set corresponding to the current plant state
+is necessarily finite, since this number cannot exceed the total number of possible active sets. However upper
+bounds on this number are unrealistically large (except in pathological cases) and hence of little use in bounding the number of times that the recursion of
+Section~\ref{sec:line:search} needs to be solved. Instead we give the typical execution time for an example
+system with an implementation in MATLAB  in section~\ref{sec:example}.
+
 \section{Example}\label{sec:example}
-In this section we present a numerical simulation for a simplified levitating ball model, as derived in 
-by~\cite{Schaich:2015}. The dynamics of the nonlinear system are given $m\ddot y = m g - c\frac{i^2}{y^2}$,
+In this section we present a numerical simulation for a simplified levitating ball model, as derived in~\cite{Schaich:2015}.
+The dynamics of the nonlinear system are given $m\ddot y = m g - c\frac{i^2}{y^2}$,
 where $m$ denotes the mass of the ball, $g$ denotes the gravitation constant, $c$ denotes a constant depending
@@
 Choosing the state $x=(y,\dot y)$ and the input $u=i$ we obtain a state space representation which depends nonlinearly
-on both the state and the input. An equilibrium is given for all $u=\sqrt{\frac{gm}{c}}x_1$.
+on both the state and the input. For any $x_1>0$, the system is in equilibrium if $x_2=0$ and $u=\sqrt{\frac{gm}{c}}x_1$.
 
@@
 %
-A representation of the form~\eqref{eq:the:problem}
+A representation of the form~\eqref{eq:the:problem}, in which the disturbance $w$ accounts for linearisation
+errors, can be obtained by sampling input and state
+constraints and using the mean-value theorem \citep[see][]{Schaich:2015}. This leads
+to a disturbance representation of the form $\mathcal W(x,u)=\{w\in\mathbb R^n: 
+\min_{k\in\mathcal S_w}\{ H_{k,i}^x x + H_{k,i}^u u\} \leq w_i \leq \max_{k\in\mathcal S_w} 
+\{ H_{k,i}^x x + H_{k,i}^u u \} \}$,
+where ${k\in\mathcal S_w}$ denotes the sample index and $i$ the row number. This point-wise polytopic representation
+together with a polyhedral representation of state constraints allows us to compute a polyhedral
+MRPI set~$\mathcal X^\infty$. As a terminal feedback controller $K$ we use the solution to the robust 
+Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2 w^Tw$ 
+with $V(x)=x^T P_0 x\geq0$, i.e. $x^TP_0x - ((A+BK)x+Dw)^TP_0((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^T w$, 
+\cite[see e.g.][]{Boyd:94}. This semi-definite program can also be used to find the minimum value of $\gamma^2$. Starting from 
+a polyhedral MRPI set~$\mathcal X^\infty$ we apply the algorithm presented in section~\ref{sec:preliminaries}
+to obtain the necessary stage constraints~$\mathcal Z_k$. At this stage we can introduce numerical values
+for individual parameters: $T_s=30\,\text{ms}$, $C=1\,\frac{\text{kg m}^3}{\text{A}^2\text{s}^2}$,
+$m=100\,\text{g}$, $\hat x_1 = 50\,\text{mm}$ and $\mathcal X=\{x:
+\abs{x_1- \hat x_1}\leq 1\,\text{mm}\wedge \abs{x_2}\leq 105\,\frac{\text{mm}}{\text{s}}\}$, $\mathcal
+U=\{u:\abs{ u-\hat u}\leq 10 \,\text{mA}\}$.
+To obtain $\mathcal W(x,u)$ we sample $\mathcal X$ and $\mathcal U$ with a total of 25 samples, i.e. the cardinality
+of $\mathcal S_w$ is 10. In the simulation we use horizon length $N=5$. We perform a cold started line search from $\chi_0=(0,0)$
+to the outer bound of the constraint set at $\chi_e=(1,-30)$, the resulting trajectories at the boundaries of
+individual active sets are plotted in figure~\ref{fig:plot}.
+
+The simulation was implemented in MATLAB only using non-optimised built-in functions for the main computational
+purposes. In the simulation illustrated in figure~\ref{fig:plot} there were a total of 10 iterations required,
+out of which 7 correspond to changes of the dominating right hand side of $\mathcal W(x,u)$, for which no
+recomputation of the solution is necessary. For $\chi_e$ on the boundary of the feasible set
+the solution time is less than $0.5\, \text{s}$ in total (using a MacBook Pro with a $2.3\,\text{GHz}$ quad-core processor).
 

### 2015-06-21 example.tex
Added review version.

@@
 We next discuss bounds on the computational complexity of the algorithm outlined in Section~\ref{sec:line:search}.
-%The computational complexity of the considered algorithm can easily be bounded. 
-%In order to give implementation-free bounds  these are expressed 
-%These are given in terms of floating point operations
-%(flops). 
 For a given active set at most $2N$ mpQPs must be solved, and this is done by decomposing the
@@
 determine $\Sigma$ in~\eqref{seq:sigma}. In the case of~\eqref{eq:sigma:normal} this requires a QR
-decomposition with $2(mn^2-n^3/3)$ floating point operations (flops), where $m$ is the number of active constraints and $n$ the number of
+decomposition with $2(mn^2-n^3/3)$ floating point operations (flops, see e.g.~\cite{Golub:1996}), 
+where $m$ is the number of active constraints and $n$ the number of
 optimisation variables, plus inversion of a triangular matrix with $(m^3-m)/6$ flops and several matrix

### 2015-06-21 post_review.tex
Added review version.

--- 2015-04-22 draft_v2.tex
@@
 $\mathcal Z_1=\{(x,u):\Xi^x_{1,i}x+\Xi^u_{1,i}u\leq\xi_{1,i},i\in\mathcal J_1\}$. The projection~$\mathcal X_1$ 
-of $\mathcal Z_1$ onto~$\mathbb R^n$ is therefore has the representation~$\mathcal X_1 = \{x:\Lambda_{1,i} x\leq\lambda_{1,i},i\in\mathcal I_1\}$.
+of $\mathcal Z_1$ onto~$\mathbb R^n$ therefore has the representation~$\mathcal X_1 = \{x:\Lambda_{1,i} x\leq\lambda_{1,i},i\in\mathcal I_1\}$.
 From here the determination of $\mathcal Z_k$ and $\mathcal X_k$ follows recursively. We are now able to formulate 
@@
 	V(\theta) = &\frac{1}{2}\theta^T M_\theta^T W M_\theta \theta + c^TM_\theta \theta \\
-& + m^TWM_\theta+\frac{1}{2}m^T Wm + c^Tm\\
+& + m^TWM_\theta \theta+\frac{1}{2}m^T Wm + c^Tm\\
 =&\frac{1}{2} \theta^T W_\theta \theta + c^T_\theta \theta + d_\theta.
@@
 	\begin{split}
-		u_N(x_N) =& \underbrace{K_{x,N}^x}_{\Psi_N^u} x_N + \underbrace{k_N^u}_{\psi_N^u}\\
-		\nu_N(x_N,\beta_N) &= \underbrace{L_{x,N}^x}_{\Psi_N^\nu} x_N + \underbrace{L_{\beta,N}^\nu}_{\Phi_N^\nu} \beta_N + 
+		u_N(x_N) =& \underbrace{K_{x,N}^u}_{\Psi_N^u} x_N + \underbrace{k_N^u}_{\psi_N^u}\\
+		\nu_N(x_N,\beta_N) &= \underbrace{L_{x,N}^\nu}_{\Psi_N^\nu} x_N + \underbrace{L_{\beta,N}^\nu}_{\Phi_N^\nu} \beta_N + 
 		\underbrace{l_N^\nu}_{\psi_N^u}\\

### 2015-06-23 post_review.tex
Made my changes.

@@
 
-In all of this work and, to the authors' best knowledge, in all of the published literature on algorithmic
+In all aforementioned work and, to the authors' best knowledge, in all of the published literature on algorithmic
 solutions to the RMPC problem, the disturbances are confined to sets that are assumed to be constant,
@@
 errors, and the approach of this paper is therefore able to handle linearisation errors in RMPC non-conservatively.
-%, as will be shown in an example.
+\textcolor{red}{\cite{Rakovic:2006} proposes an algorithm with which reachable sets can be computed when the disturbance
+is a realisation of a set defined on the product space of the disturbance the state and the input, i.e. rather
+then an explicit dependence of the set on the state and input it is implicit. Hence the work discussed in
+this paper is not covered by the analysis by~\cite{Rakovic:2006}.}
 
+This paper is structured as follows: 
 After describing the control problem in Section~\ref{sec:problem:statement} we summarise preliminary 
@@
 where $A,B,D$ are real matrices of appropriate dimension, $x,  x^+\in\mathcal X\subseteq\mathbb R^n$ denote the state 
-and successor state respectively, $u\in\mathcal U=\{u:Fu\leq{\bf{1}}\}\subset\mathbb R^p$ is the control input
-and $w\in\mathcal W(x,u)\subset\mathbb R^q$ is an unknown disturbance input. The disturbance set $\mathcal
+and successor state respectively, $u\in\mathcal U=\{u:F_iu\leq 1\,\forall i\in\mathcal I^{\mathcal U}\}
+\subset\mathbb R^p$ is the control input
+and $w\in\mathcal W(x,u)\subset\mathbb R^q$ is an unknown disturbance input, $\mathcal I^{\mathcal U}$ denotes
+the index set of the constraint set~$\mathcal U$. The disturbance set $\mathcal
 W(x,u)$ is assumed to have a known dependence on the values of $x$ and $u$, according to
@@
 \begin{equation}\label{eq:quadratic:cost}
-\sum_{k=0}^\infty \bigl( \|x_k\|_Q^2 + \|u_k\|_R^2 - \gamma^2 \|w_k\|^2 \bigr) ,
+\sum_{k=0}^\infty \bigl( \norm{x_k}_Q^2 + \norm{u_k}_R^2 - \gamma^2 \norm{w_k}^2 \bigr) ,
 \end{equation}
-where the subscript $k$ denotes the realisation of a variable at time $k$, $\|x\|_Q^2$ denotes the quadratic
+where the subscript $k$ denotes the realisation of a variable at time $k$, $\norm{x}_Q^2$ denotes the quadratic
 form $x^TQx$, $Q$ and $R$ are given positive definite
@@
 Thus the constraints $(x,u)\in\mathcal Z_m$ ensure that the terminal state, namely $x^+$ at $m=1$, is
-contained in $\mathcal{X}^\infty$.
-We define $\mathcal{X}^\infty$ as the maximal robust positive invariant (MRPI) set \citep{blanchini:2007}), for the closed-loop system governed by a fixed state feedback controller
-$u=Kx$:
+contained in $\mathcal{X}^\infty$. We define $\mathcal{X}^\infty$ as the maximal robust positive invariant 
+(MRPI) set \citep{blanchini:2007}), for the closed-loop system governed by a fixed stabilising\NOTE{Really?! We don't really need it to be stabilising for this definition} state feedback 
+controller $u=Kx$:
 %
@@
 \section{Controllable sets}\label{sec:preliminaries}
-In this section we summarise results on controllable sets that allow the constraints of the problem~\eqref{eq:the:problem} to be to formulated
-in a convenient way. The following result shows that the MRPI set (\ref{eq:definition:MRPI:set}) associated
-with the pointwise polytopic set~\eqref{eq:PWA:def:disturbance} is polytopic if $H$ is elementwise convex and
-piecewise affine. For a proof and detailed discussion of this result we refer the reader
-to~\cite{Schaich:2015}.
+In this section we summarise results on controllable sets that allow the constraints of the problem~\eqref{eq:the:problem} 
+to be to formulated in a convenient way. The following result shows that the MRPI set (\ref{eq:definition:MRPI:set}) 
+associated with the pointwise polytopic set~\eqref{eq:PWA:def:disturbance} is polytopic if $H$ is elementwise convex 
+and piecewise affine. For a proof and detailed discussion of this result we refer the reader to~\cite{Schaich:2015}.
 %
@@
 Therefore the set $\mathcal Z_1$ has a representation
-$\mathcal Z_1=\{(x,u):\Xi^x_{1,i}x+\Xi^u_{1,i}u\leq\xi_{1,i},i\in\mathcal J_1\}$. The projection~$\mathcal X_1$ 
+$\mathcal Z_1=\{(x,u):\Xi^x_{1,i}x+\Xi^u_{1,i}u\leq\xi_{1,i},i\in\mathcal J_1\}$, with~$\mathcal J_1$ denoting
+its index set. The projection~$\mathcal X_1$ 
 of $\mathcal Z_1$ onto~$\mathbb R^n$ therefore has the representation~$\mathcal X_1 = \{x:\Lambda_{1,i} x\leq\lambda_{1,i},i\in\mathcal I_1\}$.
@@
 representation~\eqref{eq:trajectory:affine:representation} is valid as long as the constraint set remains
-unchanged, i.e.\ the inequalities that hold with equality do not change. Starting from the known set of active
+unchanged, i.e.\ the inequalities that hold with equality do not change.
+\textcolor{red}{With~\eqref{eq:trajectory:affine:representation} we can justify the proposed choice of the degeneracy parameters
+$\beta_m$ and $\hat\beta_m$. When constraints are activated their dual variable starts at zero and changes
+in an affine way in the appropriate direction, at the moment a linearly dependent constraint is activated, i.e. the
+constraints become rank deficient, three things happen: The dual variable to the degenerate constraint suddenly
+depends on an additional degeneracy parameter, a compatibility constraint is introduced in the predecessor
+problem and that compatibility constraint's dual variable is given as a affine function starting at zero,
+the remaining problem is not affected by the degeneracy. By the proposed choice we couple
+the degeneracy variable to dual variable of the associated compatibility constraint, hence adding an 
+additional affine function to the already affine representation of the dual variable and thereby ensuring continuity
+of the dual variable.}
+
+Starting from the known set of active
 constraints at $\chi_0$ we perform a line search towards $\chi_e$, i.e. we vary
@@
 smallest $\alpha$ such that $\Xi_{m,i}^x x_m(x_N(\alpha))+\Xi_{m,i}^u u_m(x_N(\alpha))=\xi_{m,i}$ or
-$G_iw_m(x_N(\alpha))=1$ or $\eta_{m,i}(x_N(\alpha),\beta_N)=0$ for some $m$ and $i$, and update the set of active
+$G_iw_m(x_N(\alpha))=1$ or $\eta_{m,i}(x_N(\alpha),\allowbreak \beta_N)=0$ for some $m$ and $i$, and update the set of active
 constraints accordingly, i.e. if an additional constraint is activated it is introduced to the equality

### 2015-06-29 example.tex
Added label to figure.
Post-review edits

@@
-%!TEX root = draft_v2.tex
+%!TEX root = post_review.tex
 \section{Complexity}\label{sec:complexity}
@@
 In this section we present a numerical simulation for a simplified levitating ball model, as derived in~\cite{Schaich:2015}.
-The dynamics of the nonlinear system are given $m\ddot y = m g - c\frac{i^2}{y^2}$,
-where $m$ denotes the mass of the ball, $g$ denotes the gravitation constant, $c$ denotes a constant depending
-on the coil, $y$ the vertical distance to the coil, the simplification is due to neglecting inductive dynamics 
-and assuming we that can influence the current~$i$ directly. Figure~\ref{fig:levitating:ball} illustrates the setup.
+\edit{The dynamics of the nonlinear system are given $m\ddot y = m g - c i^2/y^2$,
+where $m$ denotes the mass of the ball, $g$ is the acceleration due to gravity, $c$ is a constant depending
+on the coil, $y$ the vertical distance to the coil (Fig.~\ref{fig:levitating:ball}).
+We assume that the current~$i$ is directly specified by the controller, thus neglecting the inductive dynamics of the coil.
+%Figure~\ref{fig:levitating:ball} illustrates the setup.
 Choosing the state $x=(y,\dot y)$ and the input $u=i$ we obtain a state space representation which depends nonlinearly
-on both the state and the input. For any $x_1>0$, the system is in equilibrium if $x_2=0$ and $u=\sqrt{\frac{gm}{c}}x_1$.
+on the state and control input.} For any $x_1>0$, the system is in equilibrium if $x_2=0$ and $u=\sqrt{\frac{gm}{c}}x_1$.
 
@@
 to the outer bound of the constraint set at $\chi_e=(1,-30)$, the resulting trajectories at the boundaries of
-individual active sets are plotted in figure~\ref{fig:plot}.
+individual active sets are plotted in Figure~\ref{fig:plot}.
 
-The simulation was implemented in MATLAB only using non-optimised built-in functions for the main computational
-purposes. In the simulation illustrated in figure~\ref{fig:plot} there were a total of 10 iterations required,
-out of which 7 correspond to changes of the dominating right hand side of $\mathcal W(x,u)$, for which no
+The simulation was implemented in MATLAB using only non-optimised built-in functions for the main computational
+purposes. In the simulation illustrated in Fig.~\ref{fig:plot} a total of $10$ iterations were required,
+of which $7$ correspond to changes of the dominating right hand side of $\mathcal W(x,u)$, for which no
 recomputation of the solution is necessary. For $\chi_e$ on the boundary of the feasible set

### 2015-06-29 post_review.tex
Post-review edits

@@
 
-In all aforementioned work and, to the authors' best knowledge, in all of the published literature on algorithmic
-solutions to the RMPC problem, the disturbances are confined to sets that are assumed to be constant,
-i.e.~independent of the system state and control inputs. Recent algorithmic advances~\citep{Schaich:2015}
-make it possible to treat polytopic disturbance sets that depend in an affine manner on the system state and the control
-input. This provides an algorithmic and analytical framework which is used in the
+\edit{In almost all existing methods for RMPC, the model disturbances are assumed to be confined to sets that are constant, i.e.~independent of the system state and control inputs.
+Disturbances that depend on model states (or control inputs) are considered in~\cite{Kuntsevich:1995,Rakovic:2006}.
+However general formulations of state and input dependence can result in non-convex constraints~\citep{Rakovic:2006}.
+To avoid this we make use of recent algorithmic advances~\citep{Schaich:2015} that enable a class of polytopic disturbance sets that depend affinely on the system state and control input to be handled using convex constraints.
+This provides an algorithmic and analytical framework which is used in the
 current paper to embed affine state and input dependent disturbance constraints into the framework of the
@@
 on model states and inputs can account for multiplicative model uncertainty as well as linearisation
-errors, and the approach of this paper is therefore able to handle linearisation errors in RMPC non-conservatively.
-\textcolor{red}{\cite{Rakovic:2006} proposes an algorithm with which reachable sets can be computed when the disturbance
-is a realisation of a set defined on the product space of the disturbance the state and the input, i.e. rather
-then an explicit dependence of the set on the state and input it is implicit. Hence the work discussed in
-this paper is not covered by the analysis by~\cite{Rakovic:2006}.}
+errors, and the approach of this paper is therefore able to handle linearisation errors in RMPC non-conservatively.}
+
+% \edit{In all aforementioned work and, to the authors' best knowledge, in all of the published literature on algorithmic
+% solutions to the RMPC problem, the disturbances are confined to sets that are assumed to be constant,
+% i.e.~independent of the system state and control inputs. Recent algorithmic advances~\citep{Schaich:2015}
+% make it possible to treat polytopic disturbance sets that depend in an affine manner on the system state and the control
+% input. This provides an algorithmic and analytical framework which is used in the
+% current paper to embed affine state and input dependent disturbance constraints into the framework of the
+% active set RMPC solver framework proposed by~\cite{Buerger:2011}. Disturbances that belong to sets which depend
+% on model states and inputs can account for multiplicative model uncertainty as well as linearisation
+% errors, and the approach of this paper is therefore able to handle linearisation errors in RMPC non-conservatively.}
+% \textcolor{red}{\cite{Rakovic:2006} proposes an algorithm with which reachable sets can be computed when the disturbance
+% is a realisation of a set defined on the product space of the disturbance the state and the input, i.e. rather
+% then an explicit dependence of the set on the state and input it is implicit. Hence the work discussed in
+% this paper is not covered by the analysis by~\cite{Rakovic:2006}.}
 
@@
 %
-where $H(x,u)$ is an elementwise convex, piecewise affine function. The control objective is to minimize the
+\edit{where each element of $H(x,u)$ is a convex, piecewise affine function for all $(x,u)\in\mathcal X\times\mathcal U$}. 
+%\edit{where $H(x,u)$ is an elementwise convex, piecewise affine function}.
+The control objective is to minimize the
 worst case value, over all future model uncertainty, of the cost
@@
 contained in $\mathcal{X}^\infty$. We define $\mathcal{X}^\infty$ as the maximal robust positive invariant 
-(MRPI) set \citep{blanchini:2007}), for the closed-loop system governed by a fixed stabilising\NOTE{Really?! We don't really need it to be stabilising for this definition} state feedback 
-controller $u=Kx$:
+(MRPI) set \citep{blanchini:2007}), for the closed-loop system
+governed by a given
+%stabilising\NOTE{Really?! We don't really need it to be stabilising for this definition} 
+state feedback controller $u=Kx$:
 %
 \begin{equation}\label{eq:definition:MRPI:set}
-	\mathcal X^\infty = \{x: (A+BK)x + Dw \in \mathcal X^\infty \forall w\in\mathcal W(x,Kx)\},
+	\mathcal X^\infty = \{x: (A+BK)x + Dw \in \mathcal X^\infty \ \forall w\in\mathcal W(x,Kx)\},
 \end{equation}
@@
 In this section we summarise results on controllable sets that allow the constraints of the problem~\eqref{eq:the:problem} 
-to be to formulated in a convenient way. The following result shows that the MRPI set (\ref{eq:definition:MRPI:set}) 
+to be formulated in a convenient way. The following result shows that the MRPI set (\ref{eq:definition:MRPI:set}) 
 associated with the pointwise polytopic set~\eqref{eq:PWA:def:disturbance} is polytopic if $H$ is elementwise convex 
@@
 %
-\begin{lem}\label{thm:MRPI:set:is:polytopic}
-Let $\mathcal X \subseteq \{x:\Gamma x\leq{\bf{1}}\wedge-\Gamma x\leq{\bf{1}}\}$ be polyhedral, and the pair $(A+BK,\Gamma)$ be
-observable, furthermore let $\mathcal W(x,Kx)$ be defined as in~\eqref{eq:PWA:def:disturbance} with a elementwise convex piecewise
-affine function $H(x,Kx)$ which is bounded for all finite $x$. Then the MRPI set $\mathcal X^\infty$ is a polytope, i.e.
-it has the representation 
+\edit{\begin{thm}[\cite{Schaich:2015}]\label{thm:MRPI:set:is:polytopic}
+Let $\mathcal X \subseteq \{x:\Gamma x\leq{\bf{1}}\wedge-\Gamma x\leq{\bf{1}}\}$ be a polyhedral set, let the pair $(A+BK,\Gamma)$ be
+observable, and let $\mathcal W(x,Kx)$ be defined as in~\eqref{eq:PWA:def:disturbance} with an elementwise convex piecewise
+affine function $H(x,Kx)$ which is bounded for all finite $x$. Then the MRPI set $\mathcal X^\infty$ is polytopic, i.e.\ it has the representation 
 \begin{equation}\label{eq:halfspace:representation:MRPI}
@@
 \end{equation}
-\end{lem}
+\end{thm}
 %
-We need to emphasise the following 
+%We need to emphasise the following 
 \begin{rem}\label{rem:vertex:representation}
-Note that an essential assumption in Lemma~\ref{thm:MRPI:set:is:polytopic} is that $\mathcal W(x,u)$ is a polytope
-for all finite $(x,u)$, i.e. it has a convex hull representation $\mathcal W(x,u) = \conv_k\{w_k(x,u)\}, k\in\{1,\dots,r\}$ where each 
+The conditions of Theorem~\ref{thm:MRPI:set:is:polytopic} require that $\mathcal W(x,u)$ is polytopic
+for all finite $(x,u)$, i.e.\ it must have a convex hull representation $\mathcal W(x,u) = \conv_k\{w_k(x,u)\}, k\in\{1,\dots,r\}$ where each 
 vertex, $w_k(x,u)$, is a piecewise affine function of $(x,u)$, i.e.
@@
 where the maximisation is performed elementwise.
-\end{rem}
+\end{rem}}
 %
 We now derive the representation of $\mathcal Z_m$ and $\mathcal X_m$ as defined in~\eqref{eq:definition:stage:constraints}.
-According to Lemma~\ref{thm:MRPI:set:is:polytopic} the MRPI set $\mathcal X^\infty$ is polytopic and has the 
+According to Theorem~\ref{thm:MRPI:set:is:polytopic} the MRPI set $\mathcal X^\infty$ is polytopic and has the 
 representation~\eqref{eq:halfspace:representation:MRPI}. Therefore the recursion~\eqref{eq:definition:mixed:stage:constraint}
@@
 \[
-	(f^T+\theta^TS^T)N_\beta \neq 0
+	(f^T+\theta^TS^T)N_\beta \neq 0 .
 \]
-and can be made arbitrarily small by the choice of $\beta$. Therefore we restrict $\theta$ to satisfy 
+%and can be made arbitrarily small by the choice of $\beta$. 
+Therefore we restrict $\theta$ to satisfy 
 \begin{equation}\label{mpQP:compatability:assumption}
@@
 and the choice of $\beta$ does not affect either the primal or the dual cost and can be used for
-any purpose. For a general mpQP, condition~\eqref{mpQP:compatability:assumption} is a restriction on the set
-of parameters for which~\eqref{mpQP:primal} has a solution of the form~\eqref{mpQP:solution}.
-In our multi-stage min-max setup, the parameter is the optimiser of a subsequent optimisation
-problem and can be ensured to satisfy~\eqref{mpQP:compatability:assumption} by the so called 
-compatibility constraint. The optimal objective of~\eqref{mpQP:primal} is given by
+any purpose. \edit{For a general mpQP, the condition~\eqref{mpQP:compatability:assumption} ensures that~\eqref{mpQP:primal}
+% is a restriction on the set
+% of parameters $\theta$ for which~\eqref{mpQP:primal} 
+has a solution of the form~\eqref{mpQP:solution}.
+In our multi-stage min-max setup, the parameter $\theta$ is the optimiser of a subsequent optimisation
+problem; hence~\eqref{mpQP:compatability:assumption} can be enforced by imposing it as a constraint (which we call a compatibility constraint) on $\theta$ in that problem.}
+%the so called compatibility constraint. 
+The optimal objective of~\eqref{mpQP:primal} is given by
 \begin{equation}\label{mpQP:cost:to:go}\begin{split}
@@
 \section{Exact solution of min-max program}\label{sec:line:search}
-The previous section presents a recursive algorithm to solve~\eqref{eq:the:problem}
+The previous section presented a recursive algorithm to solve~\eqref{eq:the:problem}
 when all active constraints are known. In this section we present a method to find the active
@@
 		&+\underbrace{N_{z,1}^{\eta}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + 
-		N_{\hat\beta,1}^\eta \psi_1^{\hat\zeta} + n_1^\eta}_{\psi_1^\eta}\\
-		&\vdots
+		N_{\hat\beta,1}^\eta \psi_1^{\hat\zeta} + n_1^\eta}_{\psi_1^\eta}
+%\\
+%		&\vdots
 	\end{split}
@@
 unchanged, i.e.\ the inequalities that hold with equality do not change.
-\textcolor{red}{With~\eqref{eq:trajectory:affine:representation} we can justify the proposed choice of the degeneracy parameters
-$\beta_m$ and $\hat\beta_m$. When constraints are activated their dual variable starts at zero and changes
-in an affine way in the appropriate direction, at the moment a linearly dependent constraint is activated, i.e. the
-constraints become rank deficient, three things happen: The dual variable to the degenerate constraint suddenly
-depends on an additional degeneracy parameter, a compatibility constraint is introduced in the predecessor
-problem and that compatibility constraint's dual variable is given as a affine function starting at zero,
-the remaining problem is not affected by the degeneracy. By the proposed choice we couple
+\textcolor{red}{With~\eqref{eq:trajectory:affine:representation} we can justify \edit{choosing the degeneracy parameters as
+$\beta_m=\zeta_{m+1}$ and $\hat\beta_m=\hat\zeta_m$. When a constraint is activated the associated dual variable starts at zero and depends affinely on $(x_N,\beta_N)$.
+%changesin an affine way in the appropriate direction, 
+When the active constraints of a sub-problem become linearly dependent three things happen: the dual variables to the degenerate constraints
+depend on an additional degeneracy parameter, a compatibility constraint is introduced in the predecessor
+problem, and that compatibility constraint's dual variable is given as a affine function starting at zero,
+while all other sub-problems are not affected by the degeneracy. Through} the proposed choice we couple
 the degeneracy variable to dual variable of the associated compatibility constraint, hence adding an 
@@
 
-Starting from the known set of active
-constraints at $\chi_0$ we perform a line search towards $\chi_e$, i.e. we vary
+Given the known set of active
+constraints at $\chi_0$ we perform a line search towards $\chi_e$ via  
 $x_N(\alpha)=\chi_0+ \alpha(\chi_e-x_0)$ for $0\leq\alpha\leq1$. We
@@
 smallest $\alpha$ such that $\Xi_{m,i}^x x_m(x_N(\alpha))+\Xi_{m,i}^u u_m(x_N(\alpha))=\xi_{m,i}$ or
-$G_iw_m(x_N(\alpha))=1$ or $\eta_{m,i}(x_N(\alpha),\allowbreak \beta_N)=0$ for some $m$ and $i$, and update the set of active
+$G_iw_m(x_N(\alpha))=1$ or $\eta_{m,i}(x_N(\alpha),\beta_N)=0$ for some $m$ and $i$, and update the set of active
 constraints accordingly, i.e. if an additional constraint is activated it is introduced to the equality
@@
 \section{Conclusion}\label{sec:conclusion}
-We have proposed a receding horizon controller for linearly constrained linear systems with unknown
-disturbances that are subject to state and input dependent bounds. The optimisation of predicted feedback laws
+This paper proposes a receding horizon controller for linearly constrained linear systems with unknown
+disturbances subject to state and input dependent bounds. The optimisation of predicted feedback laws
 is performed using an efficient specialised active set solver. Future work will consider how to limit the number of active set changes while retaining
-the guarantee of closed loop stability.
+a guarantee of closed loop stability.
 

### 2015-06-29 example.tex
Removed highlighting.

@@
 In this section we present a numerical simulation for a simplified levitating ball model, as derived in~\cite{Schaich:2015}.
-\edit{The dynamics of the nonlinear system are given $m\ddot y = m g - c i^2/y^2$,
+The dynamics of the nonlinear system are given $m\ddot y = m g - c i^2/y^2$,
 where $m$ denotes the mass of the ball, $g$ is the acceleration due to gravity, $c$ is a constant depending
@@
 Choosing the state $x=(y,\dot y)$ and the input $u=i$ we obtain a state space representation which depends nonlinearly
-on the state and control input.} For any $x_1>0$, the system is in equilibrium if $x_2=0$ and $u=\sqrt{\frac{gm}{c}}x_1$.
+on the state and control input. For any $x_1>0$, the system is in equilibrium if $x_2=0$ and $u=\sqrt{\frac{gm}{c}}x_1$.
 

### 2015-06-29 post_review.tex
Removed highlighting.

@@
 horizon is split into stages and the actions of controller and adversary at each stage depend on the
-outcome of the previous stage).
-Theoretical properties of these controllers are well understood \citep[e.g.][]{Mayne:2000}.
-However, the numerical computation of robust model predictive controllers still poses
+outcome of the previous stage). Theoretical properties of these controllers are well 
+understood \citep[e.g.][]{Mayne:2000}. However, the numerical computation of robust model predictive 
+controllers still poses
 a challenge and only few tractable solutions have been proposed.
@@
 
-\edit{In almost all existing methods for RMPC, the model disturbances are assumed to be confined to sets that are constant, i.e.~independent of the system state and control inputs.
-Disturbances that depend on model states (or control inputs) are considered in~\cite{Kuntsevich:1995,Rakovic:2006}.
-However general formulations of state and input dependence can result in non-convex constraints~\citep{Rakovic:2006}.
-To avoid this we make use of recent algorithmic advances~\citep{Schaich:2015} that enable a class of polytopic disturbance sets that depend affinely on the system state and control input to be handled using convex constraints.
-This provides an algorithmic and analytical framework which is used in the
+In almost all existing methods for RMPC, the model disturbances are assumed to be confined to sets that are constant, 
+i.e.~independent of the system state and control inputs. Disturbances that depend on model states (or control inputs) 
+are considered in~\cite{Kuntsevich:1995,Rakovic:2006}. However general formulations of state and input dependence can 
+result in non-convex constraints~\citep{Rakovic:2006}. To avoid this we make use of recent algorithmic 
+advances~\citep{Schaich:2015} that enable a class of polytopic disturbance sets that depend affinely on the system 
+state and control input to be handled using convex constraints. This provides an algorithmic and analytical framework 
+which is used in the
 current paper to embed affine state and input dependent disturbance constraints into the framework of the
@@
 on model states and inputs can account for multiplicative model uncertainty as well as linearisation
-errors, and the approach of this paper is therefore able to handle linearisation errors in RMPC non-conservatively.}
+errors, and the approach of this paper is therefore able to handle linearisation errors in RMPC non-conservatively.
 
@@
 %
-\edit{where each element of $H(x,u)$ is a convex, piecewise affine function for all $(x,u)\in\mathcal X\times\mathcal U$}. 
+where each element of $H(x,u)$ is a convex, piecewise affine function for all $(x,u)\in\mathcal X\times\mathcal U$. 
 %\edit{where $H(x,u)$ is an elementwise convex, piecewise affine function}.
@@
 %
-\edit{\begin{thm}[\cite{Schaich:2015}]\label{thm:MRPI:set:is:polytopic}
+\begin{thm}[\cite{Schaich:2015}]\label{thm:MRPI:set:is:polytopic}
 Let $\mathcal X \subseteq \{x:\Gamma x\leq{\bf{1}}\wedge-\Gamma x\leq{\bf{1}}\}$ be a polyhedral set, let the pair $(A+BK,\Gamma)$ be
@@
 where the maximisation is performed elementwise.
-\end{rem}}
+\end{rem}
 %
@@
 and the choice of $\beta$ does not affect either the primal or the dual cost and can be used for
-any purpose. \edit{For a general mpQP, the condition~\eqref{mpQP:compatability:assumption} ensures that~\eqref{mpQP:primal}
+any purpose. For a general mpQP, the condition~\eqref{mpQP:compatability:assumption} ensures that~\eqref{mpQP:primal}
 % is a restriction on the set
@@
 In our multi-stage min-max setup, the parameter $\theta$ is the optimiser of a subsequent optimisation
-problem; hence~\eqref{mpQP:compatability:assumption} can be enforced by imposing it as a constraint (which we call a compatibility constraint) on $\theta$ in that problem.}
+problem; hence~\eqref{mpQP:compatability:assumption} can be enforced by imposing it as a constraint (which we call a compatibility constraint) on $\theta$ in that problem.
 %the so called compatibility constraint. 
@@
 unchanged, i.e.\ the inequalities that hold with equality do not change.
-\textcolor{red}{With~\eqref{eq:trajectory:affine:representation} we can justify \edit{choosing the degeneracy parameters as
+With~\eqref{eq:trajectory:affine:representation} we can justify choosing the degeneracy parameters as
 $\beta_m=\zeta_{m+1}$ and $\hat\beta_m=\hat\zeta_m$. When a constraint is activated the associated dual variable starts at zero and depends affinely on $(x_N,\beta_N)$.
@@
 problem, and that compatibility constraint's dual variable is given as a affine function starting at zero,
-while all other sub-problems are not affected by the degeneracy. Through} the proposed choice we couple
+while all other sub-problems are not affected by the degeneracy. Through the proposed choice we couple
 the degeneracy variable to dual variable of the associated compatibility constraint, hence adding an 
 additional affine function to the already affine representation of the dual variable and thereby ensuring continuity
-of the dual variable.}
+of the dual variable.
 

### 2015-06-30 example.tex
Modified example.

@@
 In this section we present a numerical simulation for a simplified levitating ball model, as derived in~\cite{Schaich:2015}.
-The dynamics of the nonlinear system are given $m\ddot y = m g - c i^2/y^2$,
+The dynamics of the nonlinear system are given by $m\ddot y = m g - c i^2/y^2$,
 where $m$ denotes the mass of the ball, $g$ is the acceleration due to gravity, $c$ is a constant depending
